---
title: "Investigating sim ideas"
author: "Arnie Seong"
date: "`r format(Sys.time(), '%d %B %Y')`"
header-includes:
  - \usepackage{bm}
  - \usepackage{xcolor}
  - \usepackage{amssymb}
output: 
  html_document:
    df_print: paged
    theme: cerulean
    highlight: tango
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: true
    code_fold: show
urlcolor: blue
params:
  retrain: FALSE
  seed: 314
editor_options: 
  chunk_output_type: console
---
<style>
  .panel-tabs{
    opacity: 1;
    background-color: #2fa4e7;
    color: #ffffff;
    position: sticky;
    top: 0
  }
</style>

```{r setup, include=FALSE, message=F, echo=F, warning=F}
# LIBRARIES----

#### plotting:
library(ggplot2)
library(gridExtra)

# #### Misc:
library(here)
library(tidyr)
library(knitr)
library(kableExtra)
library(dplyr)

# model packages
library(torch)

# DOCUMENT SETUP ----
# detect pdf/html output, set chunk options, sci.notation 
latex_out <- knitr::is_latex_output()
knitr::opts_chunk$set(
  cache = FALSE, 
  message = FALSE, 
  echo = !knitr::is_latex_output(), 
  warning = FALSE
)


if (knitr::is_latex_output()) {
  knitr::opts_chunk$set(fig.height=4, 
                        fig.width=6)
} else {
  knitr::opts_chunk$set(out.width = "100%")
}

options(scipen=10)

# PANELSET
xaringanExtra::use_panelset()
xaringanExtra::style_panelset_tabs(font_family = "inherit")



# TEXT/TABLE FORMATTING----

custom_purple <- ifelse(
  knitr::is_latex_output(),
  "purple",
  "#b51ced"
)

custom_blue <- ifelse(
  knitr::is_latex_output(),
  "blue",
  "#11579e"
)

colorize <- function(x, color=custom_purple) {
  # text color conditional on latex/html output
  # from rmarkdown cookbook
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{ %s}{ %s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color, x)
  } else x
}

cat_color <- function(txt, style = 1, color = 36){
  cat(
    paste0(
      "\033[0;",
      style, ";",
      color, "m",
      txt,
      "\033[0m","\n"
    )
  )  
}

# kable NA handling
options(knitr.kable.NA = '')

# mykable function
mykable <- function(tab, cap,
                    latex_options=c("hold_position", "scale_down", "striped"), 
                    bootstrap_options=c("striped", "hover", "condensed"), 
                    full_width=F, position="center", ...){
  # kable formatting conditional on latex or html output
  if (is.null(getOption("knitr.in.progress"))){
    print(tab)
  } else if (knitr::is_latex_output()){
    kable(x=tab, caption=cap, ...) %>%
      kableExtra::kable_styling(latex_options = latex_options)
  } else if (knitr::is_html_output()){
    kable(x=tab, caption=cap, ...) %>%
      kableExtra::kable_styling(bootstrap_options = bootstrap_options, full_width=full_width, position=position)
  }
}

# notin
`%notin%` <- Negate(`%in%`)

source(here("Rcode", "torch_horseshoe_klcorrected.R"))
source(here("Rcode", "sim_functions.R"))
source(here("Rcode", "analysis_fcns.R"))
```



```{r SETUP_AND_FCNS}
knitr::opts_chunk$set(echo = FALSE)

gen_header <- function(sim_res, hlevel = 4){
  cat(
    "\n\n",  rep("#", hlevel), " sim_id ", 
    sim_res$sim_params$sim_seeds[sim_res$sim_ind], 
    sep = ""
  )
}

sim_characteristics <- function(sim_params, reduced = TRUE) {
  chars <- list(
      # sim_desc --- note: not always accurate
      "description" = sim_params[[1]],
      # data characteristics
      "overall_seed" = sim_params$seed,
      "individual_seeds" = sim_params$sim_seeds,
      "n_obs" = sim_params$n_obs,
      "err_sig" = sim_params$err_sig,
      "xdist" = sim_params$xdist,
      "fcn_plt" = plot_datagen_fcns(sim_params$flist),
      
      # nn characteristics
      "prior_tau" = sim_params$prior_tau,
      "nn_layer_dims" = do.call(c, sim_params[grepl("d_", names(sim_params))]),
      
      # training characteristics
      "n_mc_samples" = sim_params$n_mc_samples,
      "batch_size" = sim_params$batch_size,
      "train_epochs" = sim_params$train_epochs,
      "lr" = sim_params$lr,
      "lr_scheduler" = !is.null(sim_params$lr_scheduler),
      "kl_scheduler" = !is.null(sim_params$kl_scheduler)
    )
  
  if (reduced){
    chars <- chars[c(4, 5, 8:15)]
  }
  
  return(chars)
}

plot_losses <- function(fnames){
  for (sim_num in 1:length(fnames)){
    load(fnames[sim_num])
    loss_df <- loss_pltfcn(sim_res)$long_df
    loss_df$sim_id <- sim_res$sim_params$sim_seeds[sim_res$sim_ind]
    
    if (sim_num == 1){
      loss_df_all <- loss_df
    } else {
      loss_df_all <- rbind(loss_df_all, loss_df)
    }
  }
  
  plt <- loss_df_all %>% 
    ggplot(
      aes(
        y = value,
        x = epoch,
        linetype = factor(sim_id),
        color = loss_type
      )
    ) + 
    geom_line() + 
    labs(
      title = paste0(
        "loss vs epochs, across ",
        length(fnames),
        " simulations"
      )
    )
  return(plt)
}
```


```{r, VIS_CHUNK, eval = FALSE}
knitr::include_graphics(png_fnames[sim_ind])
kmat_global <- kappamat_from_sim_res(sim_res)
kmat_local <- kappamat_from_sim_res(sim_res, type = "local")

loss_pltfcn(sim_res, burn = 0)$long_df %>% 
  ggplot(
    aes(
      y = value,
      x = epoch,
      color = loss_type
    )
  ) + 
  geom_line() + 
  labs(
    title = paste0(
      "loss vs epochs"
    )
  )

loss_pltfcn(sim_res, burn = 1e4)$mse_plt
loss_pltfcn(sim_res, burn = 1e4)$kl_plt

varmat_pltfcn(
    sim_res$alpha_mat,
    y_name = "alpha",
    burn = 0
  )$all_vars_plt

varmat_pltfcn(
  kmat_global,
  y_name = "GLOBAL kappa",
  burn = 0
)$all_vars_plt


varmat_pltfcn(
  kmat_local,
  y_name = "LOCAL kappa",
  burn = 0
)$all_vars_plt


if (!is.null(sim_res$kappa_tc_mat)){
  # didn't add tau-corrected kappas to sims until later
  varmat_pltfcn(
    sim_res$kappa_tc_mat,
    y_name = "tau-corrected kappas",
    burn = 0
  )$all_vars_plt
}

if (!is.null(sim_res$kappa_fc_mat)){
  # didn't add frob-corrected kappas to sims until later
  varmat_pltfcn(
    sim_res$kappa_fc_mat,
    y_name = "frobenius-corrected kappas",
    burn = 0
  )$all_vars_plt
}

err_by_max_bfdr(kmat_local[nrow(kmat_local), ])$plt_fdrs +
  labs(
    subtitle = "using local kappas as dropout probabilities"
  )
err_by_max_bfdr(kmat_global[nrow(kmat_global), ])$plt_fdrs +
  labs(
    subtitle = "using global kappas as dropout probabilities"
  )

if (!is.null(sim_res$kappa_tc_mat)){
  err_by_max_bfdr(get_kappas_taucorrected(nn_mod))$plt_fdrs +
    labs(
      subtitle = "tau-corrected kappas as dropout probabilities"
    )
}


err_by_max_bfdr(get_kappas_frobcorrected(nn_mod))$plt_fdrs +
    labs(
      subtitle = "frob-corrected kappas as dropout probabilities"
    )



```



# purpose

- look at saved kappa mats

- investigate corrections:
  - square-rooted vs non tau correction  
  - investigate spectal norm correction

- investigate why detlayer 10k sims do worse than 1k


- 


## fnames

1k obs

[x] detlayers_5161250obs_

[x] detlayers_516_mc51250obs_

[x] detlayers_532_minibatch1250obs_

[x] detlayers_532_test1250obs_

[x] detlayers_5816_1250obs_160986


10k obs

[x] detlayers_532_minibatch12500obs_160986

[x] detlayers_532_12500obs_160986



# 10k sim Frob norms

The 10k obs sims with det layers all had extremely weird frobenius norm BFDR results.  

```{r 10ksims_setup}
stem <- here::here("sims", "results", "detlayers_532_minibatch12500obs_")
png_suffix <- c("_e1e+05")
# extract sim information from first in series
first_sim <- paste0(stem, "160986.RData")
```


```{r PRELOAD}
sim_ind <- 0
load(first_sim)
seeds <- sim_res$sim_params$sim_seeds
res_fnames <- paste0(stem, seeds, ".RData")
png_fnames <- paste0(stem, seeds, png_suffix, ".png")
mod_fnames <- paste0(stem, seeds, ".pt")
sim_characteristics(sim_res$sim_params)
```

```{r LOAD_NEXT}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
```

```{r}

tau_correction_factor <- tau_correction(nn_mod)  # square-rooted tau correction factor
get_kappas_taucorrected # uses squarerooted correction

ztilsq_1 <- get_ztil_sq(nn_mod$fc1)
zsq_1 <- get_zsq(nn_mod$fc1)
ztilsq_1 / zsq_1

kt_1 <- (1 + zsq_1 * tau_correction_factor^4)^(-1)



get_spectral_norms <- function(nn_mod, verbose = FALSE){
  l_names <- names(nn_mod$children)
  L <- length(nn_mod$children)
  spec_norms <- rep(1, length(l_names))
  names(spec_norms) <- l_names
  for (l in 1:L){
    if (grepl("fc", l_names[l])){
      if (verbose) {cat("hshoe layer ", l_names[l])}
      # get spectral norm of ZW
      W <- as_array(nn_mod$children[[l]]$weight_mu)
      Z <- diag(sqrt(get_zsq(nn_mod$children[[l]])))
      ZW <- Z%*%t(W)
      spec_norms[l] <- max(svd(ZW)$d[1])
    } else {
      if (verbose) {cat("det layer ", l_names[l])}
      w <- as_array(nn_mod$children[[l]]$weight)
      spec_norms[l] <- max(svd(w)$d[1])
      # get spectral norm of W
    }
  }
  return(spec_norms)
}

get_specnorm_correction <- function(nn_mod, prod_fcn = prod){
  sn_vec <- get_spectral_norms(nn_mod)
  prod_fcn(sn_vec[2:length(sn_vec)])
}
get_kappas_specnormcorrected <- function(nn_mod, prod_fcn = prod){
  zsq_1 <- get_zsq(nn_mod$fc1)
  sn_correction <- get_specnorm_correction(nn_mod, prod_fcn)
  return((1 + zsq_1*sn_correction^2)^(-1))
}

get_composite_specnorm <- function(nn_mod){
  l_names <- names(nn_mod$children)
  L <- length(nn_mod$children)
  for (l in 2:L){
    if (grepl("fc", l_names[l])){
      W <- as_array(nn_mod$children[[l]]$weight_mu)
      Z <- diag(sqrt(get_zsq(nn_mod$children[[l]])))
      current_W <- Z%*%t(W)
    } else {
      current_W <- as_array(nn_mod$children[[l]]$weight)
    }
    
    if (l==2){
      prev_W <- current_W
    } else {
      prev_W <- prev_W %*% t(current_W)
    }
  }
  return(svd(prev_W)$d[1])
}

get_kappas_compositespecnorm <- function(nn_mod){
  zsq_1 <- get_zsq(nn_mod$fc1)
  sn_correction <- get_composite_specnorm(nn_mod)
  return((1 + zsq_1*sn_correction^2)^(-1)) 
}


kl_1 <- get_kappas(nn_mod$fc1, type = "local")
ksn_1 <- get_kappas_specnormcorrected(nn_mod, prod_fcn = prod)
kcsn_1 <- get_kappas_compositespecnorm(nn_mod)
kt_1 <- get_kappas_taucorrected(nn_mod)

cbind(kl_1, ksn_1, kcsn_1, kt_1)
```








# saved kappa mats

- want to see if stopping earlier is better.  Needs to be after KL has stopped being annealed, then want to choose either based on lowest KL, lowest MSE gap, or lowest test MSE?

- good sims based on last epoch performance


- not great sims based on last epoch performance




```{r}

```









# 1000 obs

## 5x16, no mc, no minibatching

- first 2 layers hshoe, rest deterministic

- single update $z$

- PV tau with $p_0 = 10$

- no minibatching 

- kl annealing only


__Comments:__

- 


```{r nomc_516}
stem <- here::here("sims", "results", "detlayers_5161250obs_")
stem <- here::here("sims", "results", "detlayers_smallbias_corr.3_5x1612500obs_")

png_suffix <- c("_e1e+05")
# extract sim information from first in series
first_sim <- paste0(stem, "155447.RData")
load(first_sim)
seeds <- sim_res$sim_params$sim_seeds
res_fnames <- paste0(stem, seeds, ".RData")
png_fnames <- paste0(stem, seeds, png_suffix, ".png")
mod_fnames <- paste0(stem, seeds, ".pt")
sim_characteristics(sim_res$sim_params)

sim_ind <- 0

# check prior tau calculation
# dim_vec <- do.call(c, sim_params[grep(pattern = "d_", names(sim_params))])
# param_scaling <- round(sim_params$n_obs * sim_params$ttsplit) / param_counts_from_dims(dim_vec)[4]
# tau0_PV(
#   p_0 = 10, d = 104, sig = 1,
#   n = round(sim_params$n_obs * sim_params$ttsplit)
# )

```


```{r}
load(res_fnames[1])
nn_mod <- torch_load(mod_fnames[1])
plot_datagen_fcns(sim_res$sim_params$flist)

```


### sims {.panelset}

```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```

