---
title: "Salary data basic EDA"
author: "Arnie Seong"
date: "`r format(Sys.time(), '%d %B %Y')`"
header-includes:
  - \usepackage{bm}
  - \usepackage{xcolor}
  - \usepackage{amssymb}
output: 
  html_document:
    df_print: paged
    theme: cerulean
    highlight: tango
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: true
    code_fold: show
urlcolor: blue
params:
  retrain: FALSE
  seed: 314
editor_options: 
  chunk_output_type: console
---
<style>
  .panel-tabs{
    opacity: 1;
    background-color: #2fa4e7;
    color: #ffffff;
    position: sticky;
    top: 0
  }
</style>

```{r setup, include=FALSE, message=F, echo=F, warning=F}
# LIBRARIES----

#### plotting:
library(ggplot2)
library(gridExtra)

# #### Misc:
library(here)
library(tidyr)
library(knitr)
library(kableExtra)
library(dplyr)

# model packages
library(torch)

# DOCUMENT SETUP ----
# detect pdf/html output, set chunk options, sci.notation 
latex_out <- knitr::is_latex_output()
knitr::opts_chunk$set(
  cache = FALSE, 
  message = FALSE, 
  echo = !knitr::is_latex_output(), 
  warning = FALSE
)


if (knitr::is_latex_output()) {
  knitr::opts_chunk$set(fig.height=4, 
                        fig.width=6)
} else {
  knitr::opts_chunk$set(out.width = "100%")
}

options(scipen=10)

# PANELSET
xaringanExtra::use_panelset()
xaringanExtra::style_panelset_tabs(font_family = "inherit")



# TEXT/TABLE FORMATTING----

custom_purple <- ifelse(
  knitr::is_latex_output(),
  "purple",
  "#b51ced"
)

custom_blue <- ifelse(
  knitr::is_latex_output(),
  "blue",
  "#11579e"
)

colorize <- function(x, color=custom_purple) {
  # text color conditional on latex/html output
  # from rmarkdown cookbook
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{ %s}{ %s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color, x)
  } else x
}

cat_color <- function(txt, style = 1, color = 36){
  cat(
    paste0(
      "\033[0;",
      style, ";",
      color, "m",
      txt,
      "\033[0m","\n"
    )
  )  
}

# kable NA handling
options(knitr.kable.NA = '')

# mykable function
mykable <- function(tab, cap,
                    latex_options=c("hold_position", "scale_down", "striped"), 
                    bootstrap_options=c("striped", "hover", "condensed"), 
                    full_width=F, position="center", ...){
  # kable formatting conditional on latex or html output
  if (is.null(getOption("knitr.in.progress"))){
    print(tab)
  } else if (knitr::is_latex_output()){
    kable(x=tab, caption=cap, ...) %>%
      kableExtra::kable_styling(latex_options = latex_options)
  } else if (knitr::is_html_output()){
    kable(x=tab, caption=cap, ...) %>%
      kableExtra::kable_styling(bootstrap_options = bootstrap_options, full_width=full_width, position=position)
  }
}

# notin
`%notin%` <- Negate(`%in%`)

source(here("Rcode", "torch_horseshoe_klcorrected.R"))
source(here("Rcode", "sim_functions.R"))
source(here("Rcode", "analysis_fcns.R"))
load(here::here("data", "salary.RData"))
```



These data were obtained from the Current Population Survey at https://www.census.gov/programs-surveys/cps.html

To use these data you should add a reference to:

Flood, Sarah and King, Miriam and Rodgers, Renae and Ruggles, Steven and Warren, J Robert (2020).
Integrated Public Use Microdata Series, Current Population Survey: Version 7.0 [dataset]
Minneapolis, MN: IPUMS, 10.18128/D030.V7.0

See https://cps.ipums.org/cps/citation.shtml for the rules regarding citation and use of the CPS database


```{r}
source("https://www.ics.uci.edu/~akseong/Rcode/EDA_R_functions.R")
kable(head(salary), caption = "head of salary data",
      format = "latex", booktabs = T, align = 'c') %>%
  kable_styling(latex_options = c("striped", "condensed")) %>%
  kableExtra::kable_styling(latex_options = "hold_position")


summtab <- table1_func(df = salary, strat.by = "female")
# returns summary table stratified by gender
# means + sd for continuous covariates
# counts + percent of total for categorical

kable(summtab, caption = "variables stratified by male/female",
      format = "latex", booktabs = T, align = 'c') %>%
  kable_styling(latex_options = c("striped", "condensed")) %>%
  add_header_above(c(" " = 1, "Mean(SD) or N (% of group total N)" = 3)) %>%
  add_header_above(c(" " = 1, "Male" = 1, "Female" = 1, "total" = 1)) %>%
  kableExtra::kable_styling(latex_options = "hold_position")
```
















