---
title: "Simulation results: deterministic layers in VC model"
author: "Arnie Seong"
date: "`r format(Sys.time(), '%d %B %Y')`"
header-includes:
  - \usepackage{bm}
  - \usepackage{xcolor}
  - \usepackage{amssymb}
output: 
  html_document:
    df_print: paged
    theme: cerulean
    highlight: tango
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: true
    code_fold: show
urlcolor: blue
params:
  retrain: FALSE
  seed: 314
editor_options: 
  chunk_output_type: console
---
<style>
  .panel-tabs{
    opacity: 1;
    background-color: #2fa4e7;
    color: #ffffff;
    position: sticky;
    top: 0
  }
</style>

```{r setup, include=FALSE, message=F, echo=F, warning=F}
# LIBRARIES----

#### plotting:
library(ggplot2)
library(gridExtra)

# #### Misc:
library(here)
library(tidyr)
library(knitr)
library(kableExtra)
library(dplyr)

# model packages
library(torch)

# DOCUMENT SETUP ----
# detect pdf/html output, set chunk options, sci.notation 
latex_out <- knitr::is_latex_output()
knitr::opts_chunk$set(
  cache = FALSE, 
  message = FALSE, 
  echo = !knitr::is_latex_output(), 
  warning = FALSE
)


if (knitr::is_latex_output()) {
  knitr::opts_chunk$set(fig.height=4, 
                        fig.width=6)
} else {
  knitr::opts_chunk$set(out.width = "100%")
}

options(scipen=10)

# PANELSET
xaringanExtra::use_panelset()
xaringanExtra::style_panelset_tabs(font_family = "inherit")



# TEXT/TABLE FORMATTING----

custom_purple <- ifelse(
  knitr::is_latex_output(),
  "purple",
  "#b51ced"
)

custom_blue <- ifelse(
  knitr::is_latex_output(),
  "blue",
  "#11579e"
)

colorize <- function(x, color=custom_purple) {
  # text color conditional on latex/html output
  # from rmarkdown cookbook
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{ %s}{ %s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color, x)
  } else x
}

cat_color <- function(txt, style = 1, color = 36){
  cat(
    paste0(
      "\033[0;",
      style, ";",
      color, "m",
      txt,
      "\033[0m","\n"
    )
  )  
}

# kable NA handling
options(knitr.kable.NA = '')

# mykable function
mykable <- function(tab, cap,
                    latex_options=c("hold_position", "scale_down", "striped"), 
                    bootstrap_options=c("striped", "hover", "condensed"), 
                    full_width=F, position="center", ...){
  # kable formatting conditional on latex or html output
  if (is.null(getOption("knitr.in.progress"))){
    print(tab)
  } else if (knitr::is_latex_output()){
    kable(x=tab, caption=cap, ...) %>%
      kableExtra::kable_styling(latex_options = latex_options)
  } else if (knitr::is_html_output()){
    kable(x=tab, caption=cap, ...) %>%
      kableExtra::kable_styling(bootstrap_options = bootstrap_options, full_width=full_width, position=position)
  }
}

# notin
`%notin%` <- Negate(`%in%`)

source(here("Rcode", "torch_horseshoe_opus.R"))
source(here("Rcode", "sim_functions.R"))
source(here("Rcode", "analysis_fcns.R"))
```



```{r SETUP_AND_FCNS}
knitr::opts_chunk$set(echo = FALSE)

gen_header <- function(sim_res, hlevel = 4){
  cat(
    "\n\n",  rep("#", hlevel), " sim_id ", 
    sim_res$sim_params$sim_seeds[sim_res$sim_ind], 
    sep = ""
  )
}
sim_characteristics <- function(sim_params, reduced = TRUE) {
  chars <- list(
      # sim_desc --- note: not always accurate
      "description" = sim_params[[1]],
      # data characteristics
      "overall_seed" = sim_params$seed,
      "individual_seeds" = sim_params$sim_seeds,
      "n_obs" = sim_params$n_obs,
      "err_sig" = sim_params$sig_eps,
      "beta_functions" = sim_params$bfcns_list,
      "p" = sim_params$p,
      "p_0" = sim_params$p_0,
      "R" = sim_params$R,
      "R_0" = sim_params$R_0,
      
      # nn characteristics
      "prior_tau" = sim_params$prior_tau,
      "nn_layer_dims" = do.call(c, sim_params[grepl("d_", names(sim_params))]),
      
      # training characteristics
      "n_mc_samples" = sim_params$n_mc_samples,
      "batch_size" = sim_params$batch_size,
      "train_epochs" = sim_params$train_epochs,
      "lr" = sim_params$lr,
      "lr_scheduler" = !is.null(sim_params$lr_scheduler),
      "kl_scheduler" = !is.null(sim_params$kl_scheduler)
    )
  
  if (reduced){
    chars <- chars[c(4, 5, 7:18)]
  }
  
  return(chars)
}

plot_losses <- function(fnames){
  for (sim_num in 1:length(fnames)){
    load(fnames[sim_num])
    loss_df <- loss_pltfcn(sim_res)$long_df
    loss_df$sim_id <- sim_res$sim_params$sim_seeds[sim_res$sim_ind]
    
    if (sim_num == 1){
      loss_df_all <- loss_df
    } else {
      loss_df_all <- rbind(loss_df_all, loss_df)
    }
  }
  
  plt <- loss_df_all %>% 
    ggplot(
      aes(
        y = value,
        x = epoch,
        linetype = factor(sim_id),
        color = loss_type
      )
    ) + 
    geom_line() + 
    labs(
      title = paste0(
        "loss vs epochs, across ",
        length(fnames),
        " simulations"
      )
    )
  return(plt)
}
```


```{r, VIS_CHUNK, eval = FALSE}
# knitr::include_graphics(png_fnames[sim_ind])

alpha_mat <- sim_res$alpha_mat
kmat_global <- sim_res$kappa_mat
kmat_local <- sim_res$kappa_local_mat
kmat_fc <- sim_res$kappa_fc_mat
kmat_tc <- sim_res$kappa_tc_mat


colnames(alpha_mat) <-
  colnames(kmat_global) <- 
  colnames(kmat_local) <- 
  colnames(kmat_fc) <- 
  colnames(kmat_tc) <- varnames


loss_pltfcn(sim_res, burn = 0)$long_df %>% 
  ggplot(
    aes(
      y = value,
      x = epoch,
      color = loss_type
    )
  ) + 
  geom_line() + 
  labs(
    title = paste0(
      "loss vs epochs"
    )
  )

loss_pltfcn(sim_res, burn = 1e4)$mse_plt
loss_pltfcn(sim_res, burn = 1e4)$kl_plt


varmat_pltfcn(
  alpha_mat,
  y_name = "alpha",
  burn = 0,
  show_vars = show_vars
)$all_vars_plt


varmat_pltfcn(
  kmat_global,
  y_name = "GLOBAL kappa",
  burn = 0,
  show_vars = show_vars
)$all_vars_plt


varmat_pltfcn(
  kmat_local,
  y_name = "LOCAL kappa",
  burn = 0,
  show_vars = show_vars
)$all_vars_plt


varmat_pltfcn(
  kmat_tc,
  y_name = "tau-corrected kappas",
  burn = 0,
  show_vars = show_vars
)$all_vars_plt

varmat_pltfcn(
  kmat_fc,
  y_name = "frobenius-corrected kappas",
  burn = 0,
  show_vars = show_vars
)$all_vars_plt

err_by_max_bfdr(
  alpha_mat[nrow(alpha_mat), ],
  true_vec = true_vars
)$plt_fdrs +
  labs(
    subtitle = "using alphas as dropout probabilities"
  )

err_by_max_bfdr(
  kmat_local[nrow(kmat_local), ],
  true_vec = true_vars
)$plt_fdrs +
  labs(
    subtitle = "using local kappas as dropout probabilities"
  )
err_by_max_bfdr(
  kmat_global[nrow(kmat_global), ],
  true_vec = true_vars
)$plt_fdrs +
  labs(
    subtitle = "using global kappas as dropout probabilities"
  )

err_by_max_bfdr(
  get_kappas_taucorrected(nn_mod),
  true_vec = true_vars
)$plt_fdrs +
  labs(
    subtitle = "tau-corrected kappas as dropout probabilities"
  )


get_kappas_frobcorrected <- function(nn_mod, ln_fcn = ln_mode, ignore_detlayers = TRUE){
  z1_c <- sqrt(get_zsq(nn_mod$fc1))
  
  for (l in 2:length(nn_mod$children)){
    # determine if hshoe or determ layer
  
    if (!is.null(nn_mod$children[[l]]$atilde_mu)) {
      # hshoe layer
      z_l <- sqrt(get_zsq(nn_mod$children[[l]]))
      if (!is.null(nn_mod$children[[l]]$weight_mu)){
        # regular hshoe layer with weights
        w_l_mu <- get_wtil_params(nn_mod$children[[l]])$wtil_mu
      } else {
        # last VC model layer (no weights)
        w_l_mu <- diag(1, length(z_l))
      }
      z1_c <- z1_c * frob(diag(z_l) %*% t(w_l_mu))
    } else {
      if (!ignore_detlayers){
      # det layer
      z1_c <- z1_c * frob(as_array(nn_mod$children[[l]]$weight))
      }
    }
    
  }
  
  return((1 + z1_c^2)^(-1))
}


err_by_max_bfdr(
  get_kappas_frobcorrected(nn_mod, ignore_detlayers = FALSE),
  true_vec = true_vars
)$plt_fdrs +
  labs(
    subtitle = "frob-corrected kappas as dropout probabilities"
  )


```



# purpose

Purpose is to see how using deterministic layers helps / hurts in VC models.  

## fnames

10k obs

[x] VCdet_vanilla532_test0sig_p3_n10k_453284

[x] VCdet_vanilla532_test0sig_tau1_p3_n10k_453284

[x] VCmod_det532_test0sig_pvtau_p3_n10k_453284

[x] VCmod_det532_test0sig_tau1_p3_n10k_453284

[x] VCbetas2_det532_sig0_p3_n10k_453284


# 10k obs

## Vanilla model, 5x32, 2 mc, minibatching

- first 2 layers hshoe, rest deterministic

- single update $z$

- PV tau with $p_0 = 10$

- no minibatching 

- kl annealing only


__Comments:__

- 


```{r vanilla_pvtau}
stem <- here::here("sims", "results", "VCdet_vanilla532_test0sig_p3_n10k_")
b0_suffix <- c("b0_e200k")
b1_suffix <- c("b1_e200k")
# extract sim information from first in series
first_sim <- paste0(stem, "453284.RData")
load(first_sim)
seeds <- sim_res$sim_params$sim_seeds
res_fnames <- paste0(stem, seeds, ".RData")
b0_fnames <- paste0(stem, seeds, b0_suffix, ".png")
b1_fnames <- paste0(stem, seeds, b1_suffix, ".png")
mod_fnames <- paste0(stem, seeds, ".pt")
sim_characteristics(sim_res$sim_params)

sim_ind <- 0

# check prior tau calculation
# dim_vec <- do.call(c, sim_params[grep(pattern = "d_", names(sim_params))])
# param_scaling <- round(sim_params$n_obs * sim_params$ttsplit) / param_counts_from_dims(dim_vec)[4]
# tau0_PV(
#   p_0 = 10, d = 104, sig = 1,
#   n = round(sim_params$n_obs * sim_params$ttsplit)
# )

```


```{r}
varnames <- c(
  paste0("z_", 1:sim_res$sim_params$R),
  paste0("x_", 1:sim_res$sim_params$p)
)

show_vars <- c(
  paste0("z_", 1:5),
  paste0("x_", 1:3)
)

true_vars <- c(
  rep(1, 5),
  rep(0, sim_res$sim_params$R-5),
  rep(1, 3),
  rep(0, sim_res$sim_params$p-3)
)
```


### sims {.panelset}

```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```





## Vanilla model, tau = 1, 5x32, 2 mc, minibatching

- first 2 layers hshoe, rest deterministic

- single update $z$

- PV tau with $p_0 = 10$

- no minibatching 

- kl annealing only


__Comments:__

- 


```{r vanilla_tau1}
stem <- here::here("sims", "results", "VCdet_vanilla532_test0sig_tau1_p3_n10k_")
b0_suffix <- c("b0_e200k")
b1_suffix <- c("b1_e200k")
# extract sim information from first in series
first_sim <- paste0(stem, "453284.RData")
load(first_sim)
seeds <- sim_res$sim_params$sim_seeds
res_fnames <- paste0(stem, seeds, ".RData")
b0_fnames <- paste0(stem, seeds, b0_suffix, ".png")
b1_fnames <- paste0(stem, seeds, b1_suffix, ".png")
mod_fnames <- paste0(stem, seeds, ".pt")
sim_characteristics(sim_res$sim_params)

sim_ind <- 0

# check prior tau calculation
# dim_vec <- do.call(c, sim_params[grep(pattern = "d_", names(sim_params))])
# param_scaling <- round(sim_params$n_obs * sim_params$ttsplit) / param_counts_from_dims(dim_vec)[4]
# tau0_PV(
#   p_0 = 10, d = 104, sig = 1,
#   n = round(sim_params$n_obs * sim_params$ttsplit)
# )

```


```{r}
varnames <- c(
  paste0("z_", 1:sim_res$sim_params$R),
  paste0("x_", 1:sim_res$sim_params$p)
)

show_vars <- c(
  paste0("z_", 1:5),
  paste0("x_", 1:3)
)

true_vars <- c(
  rep(1, 5),
  rep(0, sim_res$sim_params$R-5),
  rep(1, 3),
  rep(0, sim_res$sim_params$p-3)
)
```


### sims {.panelset}

```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```







# VC model



## VC mod + det layers

- first 2 layers hshoe, rest deterministic

- single update $z$

- PV tau with $p_0 = 10$

- no minibatching 

- kl annealing only


__Comments:__

- 


```{r vcmod_det}
stem <- here::here("sims", "results", "VCmod_det532_test0sig_pvtau_p3_n10k_")
b0_suffix <- c("b0_e200k")
b1_suffix <- c("b1_e200k")
# extract sim information from first in series
first_sim <- paste0(stem, "453284.RData")
load(first_sim)
seeds <- sim_res$sim_params$sim_seeds
res_fnames <- paste0(stem, seeds, ".RData")
b0_fnames <- paste0(stem, seeds, b0_suffix, ".png")
b1_fnames <- paste0(stem, seeds, b1_suffix, ".png")
mod_fnames <- paste0(stem, seeds, ".pt")
sim_characteristics(sim_res$sim_params)

sim_ind <- 0

# check prior tau calculation
# dim_vec <- do.call(c, sim_params[grep(pattern = "d_", names(sim_params))])
# param_scaling <- round(sim_params$n_obs * sim_params$ttsplit) / param_counts_from_dims(dim_vec)[4]
# tau0_PV(
#   p_0 = 10, d = 104, sig = 1,
#   n = round(sim_params$n_obs * sim_params$ttsplit)
# )

```


```{r}
varnames <- colnames(sim_res$alpha_mat)
show_vars <- c(
  paste0("z", 1:5),
  "b_int", "b1", "b2", "b3"
)
true_vars <- varnames %in% show_vars
```


### sims {.panelset}

```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```






## VC mod + det layers, tau = 1

- first 2 layers hshoe, rest deterministic

- single update $z$

- PV tau with $p_0 = 10$

- no minibatching 

- kl annealing only


__Comments:__

- 


```{r vcmod_det_tau1}
stem <- here::here("sims", "results", "VCmod_det532_test0sig_tau1_p3_n10k_")
b0_suffix <- c("b0_e200k")
b1_suffix <- c("b1_e200k")
# extract sim information from first in series
first_sim <- paste0(stem, "453284.RData")
load(first_sim)
seeds <- sim_res$sim_params$sim_seeds
res_fnames <- paste0(stem, seeds, ".RData")
b0_fnames <- paste0(stem, seeds, b0_suffix, ".png")
b1_fnames <- paste0(stem, seeds, b1_suffix, ".png")
mod_fnames <- paste0(stem, seeds, ".pt")
sim_characteristics(sim_res$sim_params)

sim_ind <- 0

# check prior tau calculation
# dim_vec <- do.call(c, sim_params[grep(pattern = "d_", names(sim_params))])
# param_scaling <- round(sim_params$n_obs * sim_params$ttsplit) / param_counts_from_dims(dim_vec)[4]
# tau0_PV(
#   p_0 = 10, d = 104, sig = 1,
#   n = round(sim_params$n_obs * sim_params$ttsplit)
# )

```


```{r}
varnames <- colnames(sim_res$alpha_mat)
show_vars <- c(
  paste0("z", 1:5),
  "b_int", "b1", "b2", "b3"
)
true_vars <- varnames %in% show_vars
```


### sims {.panelset}

```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```






## VC betas + det layers

- first 2 layers hshoe, rest deterministic

- single update $z$

- PV tau with $p_0 = 10$

- no minibatching 

- kl annealing only


__Comments:__

- 


```{r vcbetas}
stem <- here::here("sims", "results", "VCbetas2_det532_sig0_p3_n10k_")
b0_suffix <- c("b0_e200k")
b1_suffix <- c("b1_e200k")
# extract sim information from first in series
first_sim <- paste0(stem, "453284.RData")
load(first_sim)
seeds <- sim_res$sim_params$sim_seeds
res_fnames <- paste0(stem, seeds, ".RData")
b0_fnames <- paste0(stem, seeds, b0_suffix, ".png")
b1_fnames <- paste0(stem, seeds, b1_suffix, ".png")
mod_fnames <- paste0(stem, seeds, ".pt")
sim_characteristics(sim_res$sim_params)

sim_ind <- 0

# check prior tau calculation
# dim_vec <- do.call(c, sim_params[grep(pattern = "d_", names(sim_params))])
# param_scaling <- round(sim_params$n_obs * sim_params$ttsplit) / param_counts_from_dims(dim_vec)[4]
# tau0_PV(
#   p_0 = 10, d = 104, sig = 1,
#   n = round(sim_params$n_obs * sim_params$ttsplit)
# )

```


```{r}
varnames <- colnames(sim_res$alpha_mat)
show_vars <- paste0("z", 1:5)
true_vars <- varnames %in% show_vars
```


### sims {.panelset}

```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


