---
title: "Simulation results: Liang fcns"
author: "Arnie Seong"
date: "`r format(Sys.time(), '%d %B %Y')`"
header-includes:
  - \usepackage{bm}
  - \usepackage{xcolor}
  - \usepackage{amssymb}
output: 
  html_document:
    df_print: paged
    theme: cerulean
    highlight: tango
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: true
    code_fold: show
urlcolor: blue
params:
  retrain: FALSE
  seed: 314
editor_options: 
  chunk_output_type: console
---
<style>
  .panel-tabs{
    opacity: 1;
    background-color: #2fa4e7;
    color: #ffffff;
    position: sticky;
    top: 0
  }
</style>

```{r setup, include=FALSE, message=F, echo=F, warning=F}
# LIBRARIES----

#### plotting:
library(ggplot2)
library(gridExtra)

# #### Misc:
library(here)
library(tidyr)
library(knitr)
library(kableExtra)
library(dplyr)

# model packages
library(torch)

# DOCUMENT SETUP ----
# detect pdf/html output, set chunk options, sci.notation 
latex_out <- knitr::is_latex_output()
knitr::opts_chunk$set(
  cache = FALSE, 
  message = FALSE, 
  echo = !knitr::is_latex_output(), 
  warning = FALSE
)


if (knitr::is_latex_output()) {
  knitr::opts_chunk$set(fig.height=4, 
                        fig.width=6)
} else {
  knitr::opts_chunk$set(out.width = "100%")
}

options(scipen=10)

# PANELSET
xaringanExtra::use_panelset()
xaringanExtra::style_panelset_tabs(font_family = "inherit")



# TEXT/TABLE FORMATTING----

custom_purple <- ifelse(
  knitr::is_latex_output(),
  "purple",
  "#b51ced"
)

custom_blue <- ifelse(
  knitr::is_latex_output(),
  "blue",
  "#11579e"
)

colorize <- function(x, color=custom_purple) {
  # text color conditional on latex/html output
  # from rmarkdown cookbook
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{ %s}{ %s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color, x)
  } else x
}

cat_color <- function(txt, style = 1, color = 36){
  cat(
    paste0(
      "\033[0;",
      style, ";",
      color, "m",
      txt,
      "\033[0m","\n"
    )
  )  
}

# kable NA handling
options(knitr.kable.NA = '')

# mykable function
mykable <- function(tab, cap,
                    latex_options=c("hold_position", "scale_down", "striped"), 
                    bootstrap_options=c("striped", "hover", "condensed"), 
                    full_width=F, position="center", ...){
  # kable formatting conditional on latex or html output
  if (is.null(getOption("knitr.in.progress"))){
    print(tab)
  } else if (knitr::is_latex_output()){
    kable(x=tab, caption=cap, ...) %>%
      kableExtra::kable_styling(latex_options = latex_options)
  } else if (knitr::is_html_output()){
    kable(x=tab, caption=cap, ...) %>%
      kableExtra::kable_styling(bootstrap_options = bootstrap_options, full_width=full_width, position=position)
  }
}

# notin
`%notin%` <- Negate(`%in%`)

source(here("Rcode", "torch_horseshoe_klcorrected.R"))
source(here("Rcode", "sim_functions.R"))
source(here("Rcode", "analysis_fcns.R"))
```



```{r SETUP_AND_FCNS}
knitr::opts_chunk$set(echo = FALSE)

gen_header <- function(sim_res, hlevel = 4){
  cat(
    "\n\n",  rep("#", hlevel), " sim_id ", 
    sim_res$sim_params$sim_seeds[sim_res$sim_ind], 
    sep = ""
  )
}

sim_characteristics <- function(sim_params) {
  chars <- list(
      # sim_desc --- note: not always accurate
      # "description" = sim_params[[1]],
      # data characteristics
      # "overall_seed" = sim_params$seed,
      # "individual_seeds" = sim_params$sim_seeds,
      "n_obs" = sim_params$n_obs,
      "err_sig" = sim_params$err_sig,
      "train_sig" = sim_params$train_sig,
      "ttsplit" = sim_params$ttsplit,
      # "xdist" = sim_params$xdist,
      # "fcn_plt" = plot_datagen_fcns(sim_params$flist),
      
      # nn characteristics
      "prior_tau" = sim_params$prior_tau,
      "nn_layer_dims" = do.call(c, sim_params[grepl("d_", names(sim_params))]),
      
      # training characteristics
      "n_mc_samples" = sim_params$n_mc_samples,
      # "batch_size" = sim_params$batch_size,
      "train_epochs" = sim_params$train_epochs,
      "lr" = sim_params$lr
      # "lr_scheduler" = !is.null(sim_params$lr_scheduler),
      # "kl_scheduler" = !is.null(sim_params$kl_scheduler)
    )
    return(chars)
}

plot_losses <- function(fnames){
  for (sim_num in 1:length(fnames)){
    load(fnames[sim_num])
    loss_df <- loss_pltfcn(sim_res)$long_df
    loss_df$sim_id <- sim_res$sim_params$sim_seeds[sim_res$sim_ind]
    
    if (sim_num == 1){
      loss_df_all <- loss_df
    } else {
      loss_df_all <- rbind(loss_df_all, loss_df)
    }
  }
  
  plt <- loss_df_all %>% 
    ggplot(
      aes(
        y = value,
        x = epoch,
        linetype = factor(sim_id),
        color = loss_type
      )
    ) + 
    geom_line() + 
    labs(
      title = paste0(
        "loss vs epochs, across ",
        length(fnames),
        " simulations"
      )
    )
  return(plt)
}
```


```{r, VIS_CHUNK, eval = FALSE}
# knitr::include_graphics(png_fnames[sim_ind])
kmat_global <- kappamat_from_sim_res(sim_res)
kmat_local <- kappamat_from_sim_res(sim_res, type = "local")

loss_pltfcn(sim_res, burn = 0)$long_df %>% 
  ggplot(
    aes(
      y = value,
      x = epoch,
      color = loss_type
    )
  ) + 
  geom_line() + 
  labs(
    title = paste0(
      "loss vs epochs"
    )
  )

loss_pltfcn(sim_res, burn = 1e4)$mse_plt
loss_pltfcn(sim_res, burn = 1e4)$kl_plt

varmat_pltfcn(
    sim_res$alpha_mat,
    y_name = "alpha",
    burn = 0,
    show_vars = show_vars
  )$all_vars_plt

varmat_pltfcn(
  kmat_global,
  y_name = "GLOBAL kappa",
  burn = 0,
  show_vars = show_vars
)$all_vars_plt


varmat_pltfcn(
  kmat_local,
  y_name = "LOCAL kappa",
  burn = 0,
  show_vars = show_vars
)$all_vars_plt


if (!is.null(sim_res$kappa_tc_mat)){
  # didn't add tau-corrected kappas to sims until later
  varmat_pltfcn(
    sim_res$kappa_tc_mat,
    y_name = "tau-corrected kappas",
    burn = 0,
    show_vars = show_vars
  )$all_vars_plt
}

if (!is.null(sim_res$kappa_fc_mat)){
  # didn't add frob-corrected kappas to sims until later
  varmat_pltfcn(
    sim_res$kappa_fc_mat,
    y_name = "frobenius-corrected kappas",
    burn = 0,
   show_vars = show_vars
  )$all_vars_plt
}

err_by_max_bfdr(kmat_local[nrow(kmat_local), ], true_vec)$plt_fdrs +
  labs(
    subtitle = "using local kappas as dropout probabilities"
  )

err_by_max_bfdr(get_kappas_sntau(nn_mod, print_vals = TRUE), true_vec)$plt_fdrs +
    labs(
      subtitle = "FC2 & composite specnorm-corrected kappas as dropout probabilities"
    )

err_by_max_bfdr(get_kappas_sntau(nn_mod, sn_type = "regular", print_vals = TRUE), true_vec)$plt_fdrs +
    labs(
      subtitle = "FC2 & reg specnorm-corrected kappas as dropout probabilities"
    )



if (!is.null(sim_res$kappa_tc_mat)){
  err_by_max_bfdr(get_kappas_taucorrected(nn_mod), true_vec)$plt_fdrs +
    labs(
      subtitle = "tau-corrected kappas as dropout probabilities"
    )
}

err_by_max_bfdr(get_kappas_frobcorrected(nn_mod), true_vec)$plt_fdrs +
    labs(
      subtitle = "frob-corrected kappas as dropout probabilities"
    )


err_by_max_bfdr(get_kappas_specnormcorrected(nn_mod), true_vec)$plt_fdrs +
    labs(
      subtitle = "specnorm-corrected kappas as dropout probabilities"
    )

err_by_max_bfdr(get_kappas_compositespecnorm(nn_mod), true_vec)$plt_fdrs +
    labs(
      subtitle = "composite specnorm-corrected kappas as dropout probabilities"
    )

err_by_max_bfdr(prob_kappas_gt_thresh(nn_mod, thresh = 0.1, correction = 1, type = "local")
  , true_vec)$plt_fdrs +
    labs(
      subtitle = "P(kappa>0.25) as dropout probabilities, no correction"
    )

err_by_max_bfdr(prob_kappas_gt_thresh(nn_mod, thresh = 0.5, correction = 1, type = "local")
  , true_vec)$plt_fdrs +
    labs(
      subtitle = "P(kappa>0.5) as dropout probabilities, no correction"
    )

err_by_max_bfdr(prob_kappas_gt_thresh(nn_mod, thresh = 0.5, correction = get_composite_specnorm(nn_mod), type = "global")
  , true_vec)$plt_fdrs +
    labs(
      subtitle = "P(kappa>0.5) as dropout probabilities, compositesn correction"
    )


err_by_max_bfdr(prob_kappas_gt_thresh(nn_mod, thresh = 0.9, correction = get_composite_specnorm(nn_mod), type = "global")
  , true_vec)$plt_fdrs +
    labs(
      subtitle = "P(kappa>0.9) as dropout probabilities, compositesn correction"
    )

```



# purpose

Purpose is to see how using deterministic layers helps / hurts.  

## fnames

p=50

det1_5x8_liangfcn1p50_500obs_144960
det1_5x8_liangfcn1p50_500obs_326454
det1_5x8_liangfcn1p50_1000obs_144960
det1_5x8_liangfcn1p50_1000obs_326454
det1_5x16_liangfcn1p50_500obs_155447
det1_5x16_liangfcn1p50_500obs_515157
det1_5x16_liangfcn1p50_1000obs_155447
det1_5x16_liangfcn1p50_1000obs_515157
det1_5x16_liangfcn1p50_2000obs_515157
det1_5x16_liangfcn1p50_2000obs_155447


p=500
det1_5x4_liangfcn1p500_500obs_144960
det1_5x4_liangfcn1p500_500obs_326454
det1_5x8_liangfcn1p500_2000obs_144960
det1_5x8_liangfcn1p500_2000obs_326454
det1_5x16_liangfcn1p500_500obs_515157
det1_5x16_liangfcn1p500_500obs_155447
det1_5x16_liangfcn1p500_1000obs_515157
det1_5x16_liangfcn1p500_1000obs_155447
det1_5x16_liangfcn1p500_5000obs_155447
det1_5x16_liangfcn1p500_5000obs_515157




all trained with no batching, only KL annealing, 5 MC samples to get expected loglikelihood, p_0 = p/10


# p=50

## 5x8, 400 train, 100 test

__Comments:__

- misses: x3, x4, sometimes x1

- MSE: 1.6 vs 2, stays between .6 of each other; train sig ~ 1.6, so good

- KL:

- alphas: strong separation, but misses x3, x4, and sometimes x1

- BFDRs: specnorm, composite specnorm have BFDR and FDR closest; frob OK

- overall:


```{r}
stem <- here::here("sims", "results", "det1_5x8_liangfcn1p50_500obs_")
png_suffix <- c("_e2e+05")
# extract sim information from first in series
first_sim <- paste0(stem, "144960.RData")
load(first_sim)
seeds <- sim_res$sim_params$sim_seeds
res_fnames <- paste0(stem, seeds, ".RData")
png_fnames <- paste0(stem, seeds, png_suffix, ".png")
mod_fnames <- paste0(stem, seeds, ".pt")
sim_characteristics(sim_res$sim_params)

sim_ind <- 0
show_vars <- paste0("x", 1:5)
true_vec = c(rep(1, 5), rep(0, 45))
```


```{r}
load(res_fnames[1])
nn_mod <- torch_load(mod_fnames[1])
prob_kappas_gt_thresh(nn_mod, thresh = 0.5, correction = 1, type = "global")
prob_kappas_gt_thresh(nn_mod, thresh = 0.5, correction = get_composite_specnorm(nn_mod), type = "global")
```


### sims {.panelset}

```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```



## 5x8, 800 train, 200 test


__Comments:__



- misses: no misses in alphas, local

- MSE: training higher than test.  .1-1.25 train; .8-1.1 test, stays between .25 of each other  

- alphas, local kappas: both great

- BFDRs: tau-corrected not great in 1 sim; frobenius fine but slightly anti-conservative; regular specnorm perfect; composite not as good

- overall:



```{r}
stem <- here::here("sims", "results", "det1_5x8_liangfcn1p50_1000obs_")
png_suffix <- c("_e2e+05")
# extract sim information from first in series
first_sim <- paste0(stem, "144960.RData")
load(first_sim)
seeds <- sim_res$sim_params$sim_seeds
res_fnames <- paste0(stem, seeds, ".RData")
png_fnames <- paste0(stem, seeds, png_suffix, ".png")
mod_fnames <- paste0(stem, seeds, ".pt")
sim_characteristics(sim_res$sim_params)

sim_ind <- 0
```


```{r}
load(res_fnames[1])
nn_mod <- torch_load(mod_fnames[1])
```


### sims {.panelset}

```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```



## 5x16, 400 train, 100 test


__Comments:__



- misses: x1, x3, x4

- MSE: train mse slightly higher, 1.2 and 1.6; test mse .8 and ~1.6

- KL:

- alphas: miss x1, x3, x4

- BFDRs:

- overall:



```{r}
stem <- here::here("sims", "results", "det1_5x16_liangfcn1p50_500obs_")
png_suffix <- c("_e2e+05")
# extract sim information from first in series
first_sim <- paste0(stem, "155447.RData")
load(first_sim)
seeds <- sim_res$sim_params$sim_seeds
res_fnames <- paste0(stem, seeds, ".RData")
png_fnames <- paste0(stem, seeds, png_suffix, ".png")
mod_fnames <- paste0(stem, seeds, ".pt")
sim_characteristics(sim_res$sim_params)

sim_ind <- 0
```


```{r}
load(res_fnames[1])
nn_mod <- torch_load(mod_fnames[1])
```


### sims {.panelset}

```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```




## 5x16, 800 train, 200 test


__Comments:__



- misses: x3, x4

- MSE: 1.6 vs 2, stays between .6 of each other  

- KL:

- alphas:

- BFDRs:

- overall:



```{r}
stem <- here::here("sims", "results", "det1_5x16_liangfcn1p50_1000obs_")
png_suffix <- c("_e2e+05")
# extract sim information from first in series
first_sim <- paste0(stem, "155447.RData")
load(first_sim)
seeds <- sim_res$sim_params$sim_seeds
res_fnames <- paste0(stem, seeds, ".RData")
png_fnames <- paste0(stem, seeds, png_suffix, ".png")
mod_fnames <- paste0(stem, seeds, ".pt")
sim_characteristics(sim_res$sim_params)

sim_ind <- 0
```


```{r}
load(res_fnames[1])
nn_mod <- torch_load(mod_fnames[1])
```


### sims {.panelset}

```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```





## 5x16, 1600 train, 400 test

__Comments:__



- misses: x3, x4

- MSE: 1.6 vs 2, stays between .6 of each other  

- KL:

- alphas:

- BFDRs:

- overall:




```{r}
stem <- here::here("sims", "results", "det1_5x16_liangfcn1p50_2000obs_")
png_suffix <- c("_e2e+05")
# extract sim information from first in series
first_sim <- paste0(stem, "515157.RData")
load(first_sim)
seeds <- sim_res$sim_params$sim_seeds
res_fnames <- paste0(stem, seeds, ".RData")
png_fnames <- paste0(stem, seeds, png_suffix, ".png")
mod_fnames <- paste0(stem, seeds, ".pt")
sim_characteristics(sim_res$sim_params)

sim_ind <- 0
```


```{r}
load(res_fnames[1])
nn_mod <- torch_load(mod_fnames[1])
```


### sims {.panelset}

```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```







# p=500



## 5x4, 400 train, 100 test

__Comments:__



- misses: x3, x4

- MSE: 1.6 vs 2, stays between .6 of each other  

- KL:

- alphas:

- BFDRs:

- overall:





```{r}
stem <- here::here("sims", "results", "det1_5x4_liangfcn1p500_500obs_")
png_suffix <- c("_e2e+05")
# extract sim information from first in series
first_sim <- paste0(stem, "144960.RData")
load(first_sim)
seeds <- sim_res$sim_params$sim_seeds
res_fnames <- paste0(stem, seeds, ".RData")
png_fnames <- paste0(stem, seeds, png_suffix, ".png")
mod_fnames <- paste0(stem, seeds, ".pt")
sim_characteristics(sim_res$sim_params)

sim_ind <- 0

show_vars <- paste0("x", 1:5)
true_vec = c(rep(1, 5), rep(0, 495))

```


```{r}
load(res_fnames[1])
nn_mod <- torch_load(mod_fnames[1])
```


### sims {.panelset}

```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```




## 5x8, 1600 train, 400 test

__Comments:__



- misses: x3, x4

- MSE: 1.6 vs 2, stays between .6 of each other  

- KL:

- alphas:

- BFDRs:

- overall:





```{r}
stem <- here::here("sims", "results", "det1_5x8_liangfcn1p500_2000obs_")
png_suffix <- c("_e2e+05")
# extract sim information from first in series
first_sim <- paste0(stem, "144960.RData")
load(first_sim)
seeds <- sim_res$sim_params$sim_seeds
res_fnames <- paste0(stem, seeds, ".RData")
png_fnames <- paste0(stem, seeds, png_suffix, ".png")
mod_fnames <- paste0(stem, seeds, ".pt")
sim_characteristics(sim_res$sim_params)

sim_ind <- 0
```


```{r}
load(res_fnames[1])
nn_mod <- torch_load(mod_fnames[1])
```


### sims {.panelset}

```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```




## 5x16, 400 train, 100 test

__Comments:__



- misses: x3, x4

- MSE: 1.6 vs 2, stays between .6 of each other  

- KL:

- alphas:

- BFDRs:

- overall:





```{r}
stem <- here::here("sims", "results", "det1_5x16_liangfcn1p500_500obs_")
png_suffix <- c("_e2e+05")
# extract sim information from first in series
first_sim <- paste0(stem, "515157.RData")
load(first_sim)
seeds <- sim_res$sim_params$sim_seeds
res_fnames <- paste0(stem, seeds, ".RData")
png_fnames <- paste0(stem, seeds, png_suffix, ".png")
mod_fnames <- paste0(stem, seeds, ".pt")
sim_characteristics(sim_res$sim_params)

sim_ind <- 0
```


```{r}
load(res_fnames[1])
nn_mod <- torch_load(mod_fnames[1])
```


### sims {.panelset}

```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```




## 5x16, 800 train, 200 test

__Comments:__



- misses: x3, x4

- MSE: 1.6 vs 2, stays between .6 of each other  

- KL:

- alphas:

- BFDRs:

- overall:





```{r}
stem <- here::here("sims", "results", "det1_5x16_liangfcn1p500_1000obs_")
png_suffix <- c("_e2e+05")
# extract sim information from first in series
first_sim <- paste0(stem, "515157.RData")
load(first_sim)
seeds <- sim_res$sim_params$sim_seeds
res_fnames <- paste0(stem, seeds, ".RData")
png_fnames <- paste0(stem, seeds, png_suffix, ".png")
mod_fnames <- paste0(stem, seeds, ".pt")
sim_characteristics(sim_res$sim_params)

sim_ind <- 0
```


```{r}
load(res_fnames[1])
nn_mod <- torch_load(mod_fnames[1])
```


### sims {.panelset}

```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```



## 5x16, 4000 train, 1000 test

__Comments:__



- misses: x3, x4

- MSE: 1.6 vs 2, stays between .6 of each other  

- KL:

- alphas:

- BFDRs:

- overall:






```{r}
stem <- here::here("sims", "results", "det1_5x16_liangfcn1p500_5000obs_")
png_suffix <- c("_e2e+05")
# extract sim information from first in series
first_sim <- paste0(stem, "155447.RData")
load(first_sim)
seeds <- sim_res$sim_params$sim_seeds
res_fnames <- paste0(stem, seeds, ".RData")
png_fnames <- paste0(stem, seeds, png_suffix, ".png")
mod_fnames <- paste0(stem, seeds, ".pt")
sim_characteristics(sim_res$sim_params)

sim_ind <- 0
```


```{r}
load(res_fnames[1])
nn_mod <- torch_load(mod_fnames[1])
```


### sims {.panelset}

```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```








