---
title: "Simulation results: deterministic layers"
author: "Arnie Seong"
date: "`r format(Sys.time(), '%d %B %Y')`"
header-includes:
  - \usepackage{bm}
  - \usepackage{xcolor}
  - \usepackage{amssymb}
output: 
  html_document:
    df_print: paged
    theme: cerulean
    highlight: tango
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: true
    code_fold: show
urlcolor: blue
params:
  retrain: FALSE
  seed: 314
editor_options: 
  chunk_output_type: console
---
<style>
  .panel-tabs{
    opacity: 1;
    background-color: #2fa4e7;
    color: #ffffff;
    position: sticky;
    top: 0
  }
</style>

```{r setup, include=FALSE, message=F, echo=F, warning=F}
# LIBRARIES----

#### plotting:
library(ggplot2)
library(gridExtra)

# #### Misc:
library(here)
library(tidyr)
library(knitr)
library(kableExtra)
library(dplyr)

# model packages
library(torch)

# DOCUMENT SETUP ----
# detect pdf/html output, set chunk options, sci.notation 
latex_out <- knitr::is_latex_output()
knitr::opts_chunk$set(
  cache = FALSE, 
  message = FALSE, 
  echo = !knitr::is_latex_output(), 
  warning = FALSE
)


if (knitr::is_latex_output()) {
  knitr::opts_chunk$set(fig.height=4, 
                        fig.width=6)
} else {
  knitr::opts_chunk$set(out.width = "100%")
}

options(scipen=10)

# PANELSET
xaringanExtra::use_panelset()
xaringanExtra::style_panelset_tabs(font_family = "inherit")



# TEXT/TABLE FORMATTING----

custom_purple <- ifelse(
  knitr::is_latex_output(),
  "purple",
  "#b51ced"
)

custom_blue <- ifelse(
  knitr::is_latex_output(),
  "blue",
  "#11579e"
)

colorize <- function(x, color=custom_purple) {
  # text color conditional on latex/html output
  # from rmarkdown cookbook
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{ %s}{ %s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color, x)
  } else x
}

cat_color <- function(txt, style = 1, color = 36){
  cat(
    paste0(
      "\033[0;",
      style, ";",
      color, "m",
      txt,
      "\033[0m","\n"
    )
  )  
}

# kable NA handling
options(knitr.kable.NA = '')

# mykable function
mykable <- function(tab, cap,
                    latex_options=c("hold_position", "scale_down", "striped"), 
                    bootstrap_options=c("striped", "hover", "condensed"), 
                    full_width=F, position="center", ...){
  # kable formatting conditional on latex or html output
  if (is.null(getOption("knitr.in.progress"))){
    print(tab)
  } else if (knitr::is_latex_output()){
    kable(x=tab, caption=cap, ...) %>%
      kableExtra::kable_styling(latex_options = latex_options)
  } else if (knitr::is_html_output()){
    kable(x=tab, caption=cap, ...) %>%
      kableExtra::kable_styling(bootstrap_options = bootstrap_options, full_width=full_width, position=position)
  }
}

# notin
`%notin%` <- Negate(`%in%`)

source(here("Rcode", "torch_horseshoe_klcorrected.R"))
source(here("Rcode", "sim_functions.R"))
source(here("Rcode", "analysis_fcns.R"))
```



```{r SETUP_AND_FCNS}
knitr::opts_chunk$set(echo = FALSE)

gen_header <- function(sim_res, hlevel = 4){
  cat(
    "\n\n",  rep("#", hlevel), " sim_id ", 
    sim_res$sim_params$sim_seeds[sim_res$sim_ind], 
    sep = ""
  )
}

sim_characteristics <- function(sim_params, reduced = TRUE) {
  chars <- list(
      # sim_desc --- note: not always accurate
      "description" = sim_params[[1]],
      # data characteristics
      "overall_seed" = sim_params$seed,
      "individual_seeds" = sim_params$sim_seeds,
      "n_obs" = sim_params$n_obs,
      "err_sig" = sim_params$err_sig,
      "xdist" = sim_params$xdist,
      "fcn_plt" = plot_datagen_fcns(sim_params$flist),
      
      # nn characteristics
      "prior_tau" = sim_params$prior_tau,
      "nn_layer_dims" = do.call(c, sim_params[grepl("d_", names(sim_params))]),
      
      # training characteristics
      "n_mc_samples" = sim_params$n_mc_samples,
      "batch_size" = sim_params$batch_size,
      "train_epochs" = sim_params$train_epochs,
      "lr" = sim_params$lr,
      "lr_scheduler" = !is.null(sim_params$lr_scheduler),
      "kl_scheduler" = !is.null(sim_params$kl_scheduler)
    )
  
  if (reduced){
    chars <- chars[c(4, 5, 8:15)]
  }
  
  return(chars)
}

plot_losses <- function(fnames){
  for (sim_num in 1:length(fnames)){
    load(fnames[sim_num])
    loss_df <- loss_pltfcn(sim_res)$long_df
    loss_df$sim_id <- sim_res$sim_params$sim_seeds[sim_res$sim_ind]
    
    if (sim_num == 1){
      loss_df_all <- loss_df
    } else {
      loss_df_all <- rbind(loss_df_all, loss_df)
    }
  }
  
  plt <- loss_df_all %>% 
    ggplot(
      aes(
        y = value,
        x = epoch,
        linetype = factor(sim_id),
        color = loss_type
      )
    ) + 
    geom_line() + 
    labs(
      title = paste0(
        "loss vs epochs, across ",
        length(fnames),
        " simulations"
      )
    )
  return(plt)
}
```


```{r, VIS_CHUNK, eval = FALSE}
knitr::include_graphics(png_fnames[sim_ind])
kmat_global <- kappamat_from_sim_res(sim_res)
kmat_local <- kappamat_from_sim_res(sim_res, type = "local")

loss_pltfcn(sim_res, burn = 0)$long_df %>% 
  ggplot(
    aes(
      y = value,
      x = epoch,
      color = loss_type
    )
  ) + 
  geom_line() + 
  labs(
    title = paste0(
      "loss vs epochs"
    )
  )

loss_pltfcn(sim_res, burn = 1e4)$mse_plt
loss_pltfcn(sim_res, burn = 1e4)$kl_plt

varmat_pltfcn(
    sim_res$alpha_mat,
    y_name = "alpha",
    burn = 0
  )$all_vars_plt

varmat_pltfcn(
  kmat_global,
  y_name = "GLOBAL kappa",
  burn = 0
)$all_vars_plt


varmat_pltfcn(
  kmat_local,
  y_name = "LOCAL kappa",
  burn = 0
)$all_vars_plt


if (!is.null(sim_res$kappa_tc_mat)){
  # didn't add tau-corrected kappas to sims until later
  varmat_pltfcn(
    sim_res$kappa_tc_mat,
    y_name = "tau-corrected kappas",
    burn = 0
  )$all_vars_plt
}

if (!is.null(sim_res$kappa_fc_mat)){
  # didn't add frob-corrected kappas to sims until later
  varmat_pltfcn(
    sim_res$kappa_fc_mat,
    y_name = "frobenius-corrected kappas",
    burn = 0
  )$all_vars_plt
}

err_by_max_bfdr(kmat_local[nrow(kmat_local), ])$plt_fdrs +
  labs(
    subtitle = "using local kappas as dropout probabilities"
  )

err_by_max_bfdr(get_kappas_sntau(nn_mod, print_vals = TRUE))$plt_fdrs +
    labs(
      subtitle = "FC2 & composite-corrected kappas as dropout probabilities"
    )

err_by_max_bfdr(get_kappas_sntau(nn_mod, sn_type = "regular", print_vals = TRUE))$plt_fdrs +
    labs(
      subtitle = "FC2 & specnorm-corrected kappas as dropout probabilities"
    )

if (!is.null(sim_res$kappa_tc_mat)){
  err_by_max_bfdr(get_kappas_taucorrected(nn_mod))$plt_fdrs +
    labs(
      subtitle = "tau-corrected kappas as dropout probabilities"
    )
}


err_by_max_bfdr(get_kappas_frobcorrected(nn_mod))$plt_fdrs +
    labs(
      subtitle = "frob-corrected kappas as dropout probabilities"
    )


err_by_max_bfdr(get_kappas_specnormcorrected(nn_mod))$plt_fdrs +
    labs(
      subtitle = "specnorm-corrected kappas as dropout probabilities"
    )

err_by_max_bfdr(get_kappas_compositespecnorm(nn_mod))$plt_fdrs +
    labs(
      subtitle = "composite specnorm-corrected kappas as dropout probabilities"
    )



```



# purpose

Purpose is to see how using deterministic layers helps / hurts.  

## fnames

1k obs

[x] detlayers_5161250obs_

[x] detlayers_516_mc51250obs_

[x] detlayers_532_minibatch1250obs_

[x] detlayers_532_test1250obs_

[x] detlayers_5816_1250obs_160986


10k obs

[x] detlayers_532_minibatch12500obs_160986

[x] detlayers_532_12500obs_160986


# 1000 obs

## 5x16, no mc, no minibatching

- first 2 layers hshoe, rest deterministic

- single update $z$

- PV tau with $p_0 = 10$

- no minibatching 

- kl annealing only


__Comments:__

- 


```{r nomc_516}
stem <- here::here("sims", "results", "detlayers_5161250obs_")
png_suffix <- c("_e1e+05")
# extract sim information from first in series
first_sim <- paste0(stem, "155447.RData")
load(first_sim)
seeds <- sim_res$sim_params$sim_seeds
res_fnames <- paste0(stem, seeds, ".RData")
png_fnames <- paste0(stem, seeds, png_suffix, ".png")
mod_fnames <- paste0(stem, seeds, ".pt")
sim_characteristics(sim_res$sim_params)

sim_ind <- 0

# check prior tau calculation
# dim_vec <- do.call(c, sim_params[grep(pattern = "d_", names(sim_params))])
# param_scaling <- round(sim_params$n_obs * sim_params$ttsplit) / param_counts_from_dims(dim_vec)[4]
# tau0_PV(
#   p_0 = 10, d = 104, sig = 1,
#   n = round(sim_params$n_obs * sim_params$ttsplit)
# )

```


```{r}
load(res_fnames[1])
nn_mod <- torch_load(mod_fnames[1])
plot_datagen_fcns(sim_res$sim_params$flist)

```


### sims {.panelset}

```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```









## 5x16, 5 mc, no minibatching

- first 2 layers hshoe, rest deterministic

- single update $z$

- PV tau with $p_0 = 10$

- no minibatching 

- kl annealing only


__Comments:__

- 


```{r mc5_516}
stem <- here::here("sims", "results", "detlayers_516_mc51250obs_") # using torch_horseshoe_opus
png_suffix <- c("_e1e+05")
# extract sim information from first in series
first_sim <- paste0(stem, "155447.RData")
load(first_sim)
seeds <- sim_res$sim_params$sim_seeds
res_fnames <- paste0(stem, seeds, ".RData")
png_fnames <- paste0(stem, seeds, png_suffix, ".png")
mod_fnames <- paste0(stem, seeds, ".pt")
sim_characteristics(sim_res$sim_params)

sim_ind <- 0

# check prior tau calculation
# dim_vec <- do.call(c, sim_params[grep(pattern = "d_", names(sim_params))])
# param_scaling <- round(sim_params$n_obs * sim_params$ttsplit) / param_counts_from_dims(dim_vec)[4]
# tau0_PV(
#   p_0 = 10, d = 104, sig = 1,
#   n = round(sim_params$n_obs * sim_params$ttsplit)
# )

```


```{r}
load(res_fnames[1])
nn_mod <- torch_load(mod_fnames[1])
plot_datagen_fcns(sim_res$sim_params$flist)

```


### sims {.panelset}

```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```






## 5x32, 2 mc samples, minibatching

- first 2 layers hshoe, rest deterministic

- single update $z$

- PV tau with $p_0 = 10$

- minibatching 

- kl annealing only


__Comments:__

- 


```{r mcmbatch_532}
stem <- here::here("sims", "results", "detlayers_532_minibatch1250obs_")
png_suffix <- c("_e2e+05")
# extract sim information from first in series
first_sim <- paste0(stem, "453598.RData")
load(first_sim)
seeds <- sim_res$sim_params$sim_seeds
res_fnames <- paste0(stem, seeds, ".RData")
png_fnames <- paste0(stem, seeds, png_suffix, ".png")
mod_fnames <- paste0(stem, seeds, ".pt")
sim_characteristics(sim_res$sim_params)

sim_ind <- 0

# check prior tau calculation
# dim_vec <- do.call(c, sim_params[grep(pattern = "d_", names(sim_params))])
# param_scaling <- round(sim_params$n_obs * sim_params$ttsplit) / param_counts_from_dims(dim_vec)[4]
# tau0_PV(
#   p_0 = 10, d = 104, sig = 1,
#   n = round(sim_params$n_obs * sim_params$ttsplit)
# )

```


```{r}
load(res_fnames[1])
nn_mod <- torch_load(mod_fnames[1])
plot_datagen_fcns(sim_res$sim_params$flist)

```


### sims {.panelset}

```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```






## 5x32, no mc, no minibatch

- first 2 layers hshoe, rest deterministic

- single update $z$

- PV tau with $p_0 = 10$

- minibatching 

- kl annealing only


__Comments:__

- 


```{r minibatch_532}
stem <- here::here("sims", "results", "detlayers_532_test1250obs_")
png_suffix <- c("_e2e+05")
# extract sim information from first in series
first_sim <- paste0(stem, "453598.RData")
load(first_sim)
seeds <- sim_res$sim_params$sim_seeds
res_fnames <- paste0(stem, seeds, ".RData")
png_fnames <- paste0(stem, seeds, png_suffix, ".png")
mod_fnames <- paste0(stem, seeds, ".pt")
sim_characteristics(sim_res$sim_params)

sim_ind <- 0

# check prior tau calculation
# dim_vec <- do.call(c, sim_params[grep(pattern = "d_", names(sim_params))])
# param_scaling <- round(sim_params$n_obs * sim_params$ttsplit) / param_counts_from_dims(dim_vec)[4]
# tau0_PV(
#   p_0 = 10, d = 104, sig = 1,
#   n = round(sim_params$n_obs * sim_params$ttsplit)
# )

```


```{r}
load(res_fnames[1])
nn_mod <- torch_load(mod_fnames[1])
plot_datagen_fcns(sim_res$sim_params$flist)

```


### sims {.panelset}

```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```



## 8-16-32-64-32, no mc, no minibatch

- first 2 layers hshoe, rest deterministic

- single update $z$

- PV tau with $p_0 = 10$

- minibatching 

- kl annealing only


__Comments:__

- 


```{r nomc_nobatch_varyingsize}
stem <- here::here("sims", "results", "detlayers_5816_1250obs_")
png_suffix <- c("_e2e+05")
# extract sim information from first in series
first_sim <- paste0(stem, "160986.RData")
load(first_sim)
seeds <- sim_res$sim_params$sim_seeds
res_fnames <- paste0(stem, seeds, ".RData")
png_fnames <- paste0(stem, seeds, png_suffix, ".png")
mod_fnames <- paste0(stem, seeds, ".pt")
sim_characteristics(sim_res$sim_params)

sim_ind <- 0

# check prior tau calculation
# dim_vec <- do.call(c, sim_params[grep(pattern = "d_", names(sim_params))])
# param_scaling <- round(sim_params$n_obs * sim_params$ttsplit) / param_counts_from_dims(dim_vec)[4]
# tau0_PV(
#   p_0 = 10, d = 104, sig = 1,
#   n = round(sim_params$n_obs * sim_params$ttsplit)
# )

```


```{r}
load(res_fnames[1])
nn_mod <- torch_load(mod_fnames[1])
plot_datagen_fcns(sim_res$sim_params$flist)

```


### sims {.panelset}

```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```






# 10k obs

## 5x32, mc + minibatching

- first 2 layers hshoe, rest deterministic

- single update $z$

- PV tau with $p_0 = 10$

- no minibatching 

- kl annealing only


__Comments:__

-  check tau, lr


```{r batch10k}
stem <- here::here("sims", "results", "detlayers_532_minibatch12500obs_")
png_suffix <- c("_e2e+05")
# extract sim information from first in series
first_sim <- paste0(stem, "160986.RData")
load(first_sim)
seeds <- sim_res$sim_params$sim_seeds
res_fnames <- paste0(stem, seeds, ".RData")
png_fnames <- paste0(stem, seeds, png_suffix, ".png")
mod_fnames <- paste0(stem, seeds, ".pt")
sim_characteristics(sim_res$sim_params)

sim_ind <- 0

# check prior tau calculation
# dim_vec <- do.call(c, sim_params[grep(pattern = "d_", names(sim_params))])
# param_scaling <- round(sim_params$n_obs * sim_params$ttsplit) / param_counts_from_dims(dim_vec)[4]
# tau0_PV(
#   p_0 = 10, d = 104, sig = 1,
#   n = round(sim_params$n_obs * sim_params$ttsplit)
# )

```


```{r}
load(res_fnames[1])
nn_mod <- torch_load(mod_fnames[1])
plot_datagen_fcns(sim_res$sim_params$flist)

```


### sims {.panelset}

```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```






## 5x32, no mc, no minibatching

- first 2 layers hshoe, rest deterministic

- single update $z$

- PV tau with $p_0 = 10$

- no minibatching 

- kl annealing only


__Comments:__

-  check tau, lr


```{r nobatch_10k}
stem <- here::here("sims", "results", "detlayers_532_12500obs_")
png_suffix <- c("_e2e+05")
# extract sim information from first in series
first_sim <- paste0(stem, "160986.RData")
load(first_sim)
seeds <- sim_res$sim_params$sim_seeds
res_fnames <- paste0(stem, seeds, ".RData")
png_fnames <- paste0(stem, seeds, png_suffix, ".png")
mod_fnames <- paste0(stem, seeds, ".pt")
sim_characteristics(sim_res$sim_params)

sim_ind <- 0

# check prior tau calculation
# dim_vec <- do.call(c, sim_params[grep(pattern = "d_", names(sim_params))])
# param_scaling <- round(sim_params$n_obs * sim_params$ttsplit) / param_counts_from_dims(dim_vec)[4]
# tau0_PV(
#   p_0 = 10, d = 104, sig = 1,
#   n = round(sim_params$n_obs * sim_params$ttsplit)
# )

```


```{r}
load(res_fnames[1])
nn_mod <- torch_load(mod_fnames[1])
plot_datagen_fcns(sim_res$sim_params$flist)

```


### sims {.panelset}

```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```












## 5x16, 5 mc, no minibatching, lr 0.001

- first 2 layers hshoe, rest deterministic

- single update $z$

- PV tau with $p_0 = 10$

- no minibatching 

- kl annealing only


__Comments:__

-  check tau, lr


```{r 516_5mc_10k}
stem <- here::here("sims", "results", "detlayers_516_12500obs_")
png_suffix <- c("_e2e+05")
# extract sim information from first in series
first_sim <- paste0(stem, "515157.RData")
load(first_sim)
seeds <- sim_res$sim_params$sim_seeds
res_fnames <- paste0(stem, seeds, ".RData")
png_fnames <- paste0(stem, seeds, png_suffix, ".png")
mod_fnames <- paste0(stem, seeds, ".pt")
sim_characteristics(sim_res$sim_params)

sim_ind <- 0

# check prior tau calculation
# dim_vec <- do.call(c, sim_params[grep(pattern = "d_", names(sim_params))])
# param_scaling <- round(sim_params$n_obs * sim_params$ttsplit) / param_counts_from_dims(dim_vec)[4]
# tau0_PV(
#   p_0 = 10, d = 104, sig = 1,
#   n = round(sim_params$n_obs * sim_params$ttsplit)
# )

```


```{r}
load(res_fnames[1])
nn_mod <- torch_load(mod_fnames[1])
plot_datagen_fcns(sim_res$sim_params$flist)

```


### sims {.panelset}

```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```





# 100 obs


## 5x16, 5 mc, no minibatching, lr 0.001

- first 2 layers hshoe, rest deterministic

- single update $z$

- PV tau with $p_0 = 10$

- no minibatching 

- kl annealing only


__Comments:__

-  check tau, lr


```{r 516_5mc_100}
stem <- here::here("sims", "results", "detlayers_516_125obs_")
png_suffix <- c("_e2e+05")
# extract sim information from first in series
first_sim <- paste0(stem, "515157.RData")
load(first_sim)
seeds <- sim_res$sim_params$sim_seeds
res_fnames <- paste0(stem, seeds, ".RData")
png_fnames <- paste0(stem, seeds, png_suffix, ".png")
mod_fnames <- paste0(stem, seeds, ".pt")
sim_characteristics(sim_res$sim_params)

sim_ind <- 0

# check prior tau calculation
# dim_vec <- do.call(c, sim_params[grep(pattern = "d_", names(sim_params))])
# param_scaling <- round(sim_params$n_obs * sim_params$ttsplit) / param_counts_from_dims(dim_vec)[4]
# tau0_PV(
#   p_0 = 10, d = 104, sig = 1,
#   n = round(sim_params$n_obs * sim_params$ttsplit)
# )

```


```{r}
load(res_fnames[1])
nn_mod <- torch_load(mod_fnames[1])
plot_datagen_fcns(sim_res$sim_params$flist)

```


### sims {.panelset}

```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```


```{r, results = "asis"}
sim_ind <- sim_ind + 1
load(res_fnames[sim_ind])
nn_mod <- torch_load(mod_fnames[sim_ind])
gen_header(sim_res)
```

```{r}
<<VIS_CHUNK>>
```






