---
title: "VC data, first sim results"
author: "Arnie Seong"
date: "`r format(Sys.time(), '%d %B %Y')`"
header-includes:
  - \usepackage{bm}
  - \usepackage{xcolor}
  - \usepackage{amssymb}
output: 
  html_document:
    df_print: paged
    theme: cerulean
    highlight: tango
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: true
    code_fold: show
urlcolor: blue
editor_options: 
  chunk_output_type: console
---

<style>
  .panel-tabs{
    opacity: 1;
    background-color: #2fa4e7;
      color: #ffffff;
      position: sticky;
    top: 0
  }
</style>
  

```{r setup, include=FALSE, message=F, echo=F, warning=F}
# LIBRARIES----

#### plotting:
library(ggplot2)
library(gridExtra)

# #### Misc:
library(here)
library(tidyr)
library(knitr)
library(kableExtra)
library(dplyr)

# model packages
library(torch)

# DOCUMENT SETUP ----
# detect pdf/html output, set chunk options, sci.notation 
latex_out <- knitr::is_latex_output()
knitr::opts_chunk$set(
  cache = FALSE, 
  message = FALSE, 
  echo = !knitr::is_latex_output(), 
  warning = FALSE
)


if (knitr::is_latex_output()) {
  knitr::opts_chunk$set(fig.height=4, 
                        fig.width=6)
} else {
  knitr::opts_chunk$set(out.width = "100%")
}

options(scipen=10)

# PANELSET
xaringanExtra::use_panelset()
xaringanExtra::style_panelset_tabs(font_family = "inherit")



# TEXT/TABLE FORMATTING----

custom_purple <- ifelse(
  knitr::is_latex_output(),
  "purple",
  "#b51ced"
)

custom_blue <- ifelse(
  knitr::is_latex_output(),
  "blue",
  "#11579e"
)

colorize <- function(x, color=custom_purple) {
  # text color conditional on latex/html output
  # from rmarkdown cookbook
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{ %s}{ %s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color, x)
  } else x
}

cat_color <- function(txt, style = 1, color = 36){
  cat(
    paste0(
      "\033[0;",
      style, ";",
      color, "m",
      txt,
      "\033[0m","\n"
    )
  )  
}

# kable NA handling
options(knitr.kable.NA = '')

# mykable function
mykable <- function(tab, cap,
                    latex_options=c("hold_position", "scale_down", "striped"), 
                    bootstrap_options=c("striped", "hover", "condensed"), 
                    full_width=F, position="center", ...){
  # kable formatting conditional on latex or html output
  if (is.null(getOption("knitr.in.progress"))){
    print(tab)
  } else if (knitr::is_latex_output()){
    kable(x=tab, caption=cap, ...) %>%
      kableExtra::kable_styling(latex_options = latex_options)
  } else if (knitr::is_html_output()){
    kable(x=tab, caption=cap, ...) %>%
      kableExtra::kable_styling(bootstrap_options = bootstrap_options, full_width=full_width, position=position)
  }
}

# notin
`%notin%` <- Negate(`%in%`)

library(torch)
source(here("Rcode", "torch_horseshoe_klcorrected.R"))
source(here("Rcode", "sim_functions.R"))
source(here("Rcode", "analysis_fcns.R"))
source(here("Rcode", "sparseVCBART_fcns.R"))
source(here("Rcode", "torch_VC_outputlayer.R"))
```





# testing the VC waters

- $Z$ dimension $R$ = 20, results only depend on first 5 $Z$ variables,

- $X$ dimension $p$ = 3,

Just to see if we can adequately capture the data generating functions, tested with $n = 10k$, noise variance $\sigma^2_\epsilon = 0$

## vanilla model

Just proceeding as usual without explicitly modeling the VC structure:


```{r FNAMES_SETUP, echo = FALSE}
stem_vanilla <- "VC_vanilla816_agnostic_test0sig_p3_n10k_"
seeds_vanilla <- c(525655, 846743)
resfile_vanilla <- here::here(
  "sims", "results", 
  paste0(stem_vanilla, seeds_vanilla, ".RData")
)
modfile_vanilla <- here::here(
  "sims", "results", 
  paste0(stem_vanilla, seeds_vanilla, ".pt")
)
# VCmod_p3_n10k_846743 and _525655

```


- 2 hidden layers, 8 and 16 units;

- $\tau_0$ agnostic for all.

```{r}
load(resfile_vanilla[1])
nn_mod <- torch_load(modfile_vanilla[1])
plot_b0_true()
plot_b1_true()

sim_res$sim_params$p_0
dim_vec <- c(
  sim_res$sim_params$d_0,
  sim_res$sim_params$d_1,
  sim_res$sim_params$d_2,
  sim_res$sim_params$d_L
)
param_counts_from_dims(dim_vec)
```



```{r PLOTTING_SETUP}
varnames <- c(
  paste0("z", 1:sim_res$sim_params$R),
  paste0("x", 1:sim_res$sim_params$p)
)
showvars <- c(
  paste0("z", 1:5),
  paste0("x", 1:sim_res$sim_params$p)
)
true_vec <- varnames %in% showvars
```


### results {.panelset}

  
  
#### sim 1
  
```{r VIS_CHUNK}
loss_pltfcn(sim_res, burn = 5e4)$mse_plt
loss_pltfcn(sim_res, burn = 5e4)$kl_plt

kmat_tc <- sim_res$kappa_tc_mat
kmat_fc <- sim_res$kappa_fc_mat
kmat_gl <- sim_res$kappa_mat
kmat_lo <- sim_res$kappa_local_mat

colnames(sim_res$alpha_mat)  <- 
  colnames(kmat_tc) <- 
  colnames(kmat_fc) <- 
  colnames(kmat_gl) <-
  colnames(kmat_lo) <- varnames

varmat_pltfcn(
  sim_res$alpha_mat,
  y_name = "alpha",
  burn = 0,
  show_vars = showvars
)$all_vars_plt

varmat_pltfcn(
  kmat_gl,
  y_name = "GLOBAL kappa",
  burn = 0,
  show_vars = showvars
)$all_vars_plt

varmat_pltfcn(
  kmat_lo,
  y_name = "LOCAL kappa",
  burn = 0,
  show_vars = showvars
)$all_vars_plt

varmat_pltfcn(
  kmat_tc,
  y_name = "tau-corrected kappas",
  burn = 0,
  show_vars = showvars
)$all_vars_plt

varmat_pltfcn(
  kmat_fc,
  y_name = "frob-corrected kappas",
  burn = 0,
  show_vars = showvars
)$all_vars_plt


err_by_max_bfdr(
  kmat_lo[nrow(kmat_lo), ],
  true_vec = true_vec
)$plt_fdrs + 
  labs(
    subtitle = "using local kappas as dropout probabilities"
  )

err_by_max_bfdr(
  kmat_gl[nrow(kmat_gl), ],
  true_vec = true_vec
)$plt_fdrs + 
  labs(
    subtitle = "using global kappas as dropout probabilities"
  )

err_by_max_bfdr(
  kmat_tc[nrow(kmat_tc),],
  true_vec = true_vec
)$plt_fdrs + 
  labs(
    subtitle = "tau-corrected kappas as dropout probabilities"
  )

err_by_max_bfdr(
  kmat_fc[nrow(kmat_fc),],
  true_vec = true_vec
)$plt_fdrs + 
  labs(
    subtitle = "frob-corrected kappas as dropout probabilities"
  )

```

#### sim 2

```{r}
load(resfile_vanilla[2])
nn_mod <- torch_load(modfile_orig[2])
<<VIS_CHUNK>>
```



## VC mod

Explicitly modeling the VC structure:

- input X, Z vars separately

- First $L-1$ layers (all but last) used to estimate $\beta_j(Z)$'s;


```{r FNAMES_SETUP, echo = FALSE}
stem_vanilla <- "VC_vanilla816_agnostic_test0sig_p3_n10k_"
seeds_vanilla <- c(525655, 846743)
resfile_vanilla <- here::here(
  "sims", "results", 
  paste0(stem_vanilla, seeds_vanilla, ".RData")
)
modfile_vanilla <- here::here(
  "sims", "results", 
  paste0(stem_vanilla, seeds_vanilla, ".pt")
)
# VCmod_p3_n10k_846743 and _525655

```


- 2 hidden layers, 8 and 16 units;

- $\tau_0$ agnostic for all.

```{r}
load(resfile_vanilla[1])
nn_mod <- torch_load(modfile_vanilla[1])
plot_b0_true()
plot_b1_true()

sim_res$sim_params$p_0
dim_vec <- c(
  sim_res$sim_params$d_0,
  sim_res$sim_params$d_1,
  sim_res$sim_params$d_2,
  sim_res$sim_params$d_L
)
param_counts_from_dims(dim_vec)
```



```{r PLOTTING_SETUP}
varnames <- c(
  paste0("z", 1:sim_res$sim_params$R),
  paste0("x", 1:sim_res$sim_params$p)
)
showvars <- c(
  paste0("z", 1:5),
  paste0("x", 1:sim_res$sim_params$p)
)
true_vec <- varnames %in% showvars
```


### results {.panelset}




```{r}
load(resfile_pvtau1[1])
nn_mod <- torch_load(modfile_pvtau1[1])
plot_datagen_fcns(sim_res$sim_params$flist)
```

## 1M epochs {.panelset}

```{r, echo = FALSE}
sim_ind = 1
```


### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_pvtau1[sim_ind])
nn_mod <- torch_load(modfile_pvtau1[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```


### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_pvtau1[sim_ind])
nn_mod <- torch_load(modfile_pvtau1[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```


### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_pvtau1[sim_ind])
nn_mod <- torch_load(modfile_pvtau1[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```


### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_pvtau1[sim_ind])
nn_mod <- torch_load(modfile_pvtau1[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```


### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_pvtau1[sim_ind])
nn_mod <- torch_load(modfile_pvtau1[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```


## 500k epochs {.panelset}

```{r, echo = FALSE}
sim_ind = 1
```


### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_pvtau2[sim_ind])
nn_mod <- torch_load(modfile_pvtau2[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```


### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_pvtau2[sim_ind])
nn_mod <- torch_load(modfile_pvtau2[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```


### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_pvtau2[sim_ind])
nn_mod <- torch_load(modfile_pvtau2[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```


### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_pvtau2[sim_ind])
nn_mod <- torch_load(modfile_pvtau2[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```


### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_pvtau2[sim_ind])
nn_mod <- torch_load(modfile_pvtau2[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```


### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_pvtau2[sim_ind])
nn_mod <- torch_load(modfile_pvtau2[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```


### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_pvtau2[sim_ind])
nn_mod <- torch_load(modfile_pvtau2[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```


### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_pvtau2[sim_ind])
nn_mod <- torch_load(modfile_pvtau2[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```


### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_pvtau2[sim_ind])
nn_mod <- torch_load(modfile_pvtau2[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```


### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_pvtau2[sim_ind])
nn_mod <- torch_load(modfile_pvtau2[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```



# smoother function set - 1k obs


```{r ONEk_FNAMES}
stem_1k_1632 <- here::here("sims", "results", "hshoe_pvtau10_correctedkappas_216321250obs_")
stem_1k_816 <- here::here("sims", "results", "hshoe_pvtau10_correctedkappas_8161250obs_")

seed_1k <- c(215244, 272835, 124107, 782699, 798186)

resfile_1k_1632 <- paste0(stem_1k_1632, seed_1k, ".RData")
modfile_1k_1632 <- paste0(stem_1k_1632, seed_1k, ".pt")

resfile_1k_816 <- paste0(stem_1k_816, seed_1k, ".RData")
modfile_1k_816 <- paste0(stem_1k_816, seed_1k, ".pt")
```

```{r}
load(resfile_1k_1632[1])
plot_datagen_fcns(sim_res$sim_params$flist)
```

## hidden layer dim: 16-32 {.panelset}

```{r, echo = FALSE}
sim_ind = 1
```


### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_1k_1632[sim_ind])
nn_mod <- torch_load(modfile_1k_1632[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```


### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_1k_1632[sim_ind])
nn_mod <- torch_load(modfile_1k_1632[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```


### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_1k_1632[sim_ind])
nn_mod <- torch_load(modfile_1k_1632[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```


### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_1k_1632[sim_ind])
nn_mod <- torch_load(modfile_1k_1632[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```


### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_1k_1632[sim_ind])
nn_mod <- torch_load(modfile_1k_1632[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```



## hidden layer dim: 8-16 {.panelset}

```{r, echo = FALSE}
sim_ind = 1
```


### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_1k_816[sim_ind])
nn_mod <- torch_load(modfile_1k_816[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```


### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_1k_816[sim_ind])
nn_mod <- torch_load(modfile_1k_816[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```


### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_1k_816[sim_ind])
nn_mod <- torch_load(modfile_1k_816[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```


### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_1k_816[sim_ind])
nn_mod <- torch_load(modfile_1k_816[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```


### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_1k_816[sim_ind])
nn_mod <- torch_load(modfile_1k_816[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```





