---
title: "VC data, first sim results"
author: "Arnie Seong"
date: "`r format(Sys.time(), '%d %B %Y')`"
header-includes:
  - \usepackage{bm}
  - \usepackage{xcolor}
  - \usepackage{amssymb}
output: 
  html_document:
    df_print: paged
    theme: cerulean
    highlight: tango
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: true
    code_fold: show
urlcolor: blue
editor_options: 
  chunk_output_type: console
---

<style>
  .panel-tabs{
    opacity: 1;
    background-color: #2fa4e7;
      color: #ffffff;
      position: sticky;
    top: 0
  }
</style>
  

```{r setup, include=FALSE, message=F, echo=F, warning=F}
# LIBRARIES----

#### plotting:
library(ggplot2)
library(gridExtra)

# #### Misc:
library(here)
library(tidyr)
library(knitr)
library(kableExtra)
library(dplyr)

# model packages
library(torch)

# DOCUMENT SETUP ----
# detect pdf/html output, set chunk options, sci.notation 
latex_out <- knitr::is_latex_output()
knitr::opts_chunk$set(
  cache = FALSE, 
  message = FALSE, 
  echo = !knitr::is_latex_output(), 
  warning = FALSE
)


if (knitr::is_latex_output()) {
  knitr::opts_chunk$set(fig.height=4, 
                        fig.width=6)
} else {
  knitr::opts_chunk$set(out.width = "100%")
}

options(scipen=10)

# PANELSET
xaringanExtra::use_panelset()
xaringanExtra::style_panelset_tabs(font_family = "inherit")



# TEXT/TABLE FORMATTING----

custom_purple <- ifelse(
  knitr::is_latex_output(),
  "purple",
  "#b51ced"
)

custom_blue <- ifelse(
  knitr::is_latex_output(),
  "blue",
  "#11579e"
)

colorize <- function(x, color=custom_purple) {
  # text color conditional on latex/html output
  # from rmarkdown cookbook
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{ %s}{ %s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color, x)
  } else x
}

cat_color <- function(txt, style = 1, color = 36){
  cat(
    paste0(
      "\033[0;",
      style, ";",
      color, "m",
      txt,
      "\033[0m","\n"
    )
  )  
}

# kable NA handling
options(knitr.kable.NA = '')

# mykable function
mykable <- function(tab, cap,
                    latex_options=c("hold_position", "scale_down", "striped"), 
                    bootstrap_options=c("striped", "hover", "condensed"), 
                    full_width=F, position="center", ...){
  # kable formatting conditional on latex or html output
  if (is.null(getOption("knitr.in.progress"))){
    print(tab)
  } else if (knitr::is_latex_output()){
    kable(x=tab, caption=cap, ...) %>%
      kableExtra::kable_styling(latex_options = latex_options)
  } else if (knitr::is_html_output()){
    kable(x=tab, caption=cap, ...) %>%
      kableExtra::kable_styling(bootstrap_options = bootstrap_options, full_width=full_width, position=position)
  }
}

# notin
`%notin%` <- Negate(`%in%`)

library(torch)
source(here("Rcode", "torch_horseshoe_klcorrected.R"))
source(here("Rcode", "sim_functions.R"))
source(here("Rcode", "analysis_fcns.R"))
source(here("Rcode", "sparseVCBART_fcns.R"))
source(here("Rcode", "torch_VC_outputlayer.R"))
```





# testing the VC waters

- $Z$ dimension $R$ = 20, results only depend on first 5 $Z$ variables,

- $X$ dimension $p$ = 3,

Just to see if we can adequately capture the data generating functions, tested with $n = 10k$, noise variance $\sigma^2_\epsilon = 0$

## vanilla model, n=10k, sig=0

Just proceeding as usual without explicitly modeling the VC structure:


```{r FNAMES_SETUP, echo = FALSE}
stem_vanilla <- "VC_vanilla816_agnostic_test0sig_p3_n10k_"
seeds_vanilla <- c(525655, 846743)
resfile_vanilla <- here::here(
  "sims", "results", 
  paste0(stem_vanilla, seeds_vanilla, ".RData")
)
modfile_vanilla <- here::here(
  "sims", "results", 
  paste0(stem_vanilla, seeds_vanilla, ".pt")
)
# VCmod_p3_n10k_846743 and _525655

data_desc <- function(sim_res){
  print(paste0("n_obs: ", sim_res$sim_params$n_obs))
  print(paste0("sig_eps: ", sim_res$sim_params$sig_eps))
  print(paste0("lr: ", sim_res$sim_params$lr))
  print(paste0("R: ", sim_res$sim_params$R))
  print(paste0("p: ", sim_res$sim_params$p))
  print(paste0("R_0: ", sim_res$sim_params$R_0))
  print(paste0("p_0: ", sim_res$sim_params$p_0))
}
```


- 2 hidden layers, 8 and 16 units;

- $\tau_0$ agnostic for all.

```{r}
load(resfile_vanilla[1])
nn_mod <- torch_load(modfile_vanilla[1])
plot_b0_true()
plot_b1_true()

data_desc(sim_res)
dim_vec <- c(
  sim_res$sim_params$d_0,
  sim_res$sim_params$d_1,
  sim_res$sim_params$d_2,
  sim_res$sim_params$d_L
)
param_counts_from_dims(dim_vec)
```



```{r PLOTTING_SETUP}
varnames <- c(
  paste0("z", 1:sim_res$sim_params$R),
  paste0("x", 1:sim_res$sim_params$p)
)
showvars <- c(
  paste0("z", 1:5),
  paste0("x", 1:sim_res$sim_params$p)
)
true_vec <- varnames %in% showvars
```


### results {.panelset}

  
  
#### sim 1
  
```{r VIS_CHUNK}
loss_pltfcn(sim_res, burn = 5e4)$mse_plt
loss_pltfcn(sim_res, burn = 5e4)$kl_plt

kmat_tc <- sim_res$kappa_tc_mat
kmat_gl <- sim_res$kappa_mat
kmat_lo <- sim_res$kappa_local_mat
kmat_fc <- sim_res$kappa_fc_mat

colnames(sim_res$alpha_mat)  <- 
  colnames(kmat_tc) <- 
  colnames(kmat_gl) <-
  colnames(kmat_lo) <- varnames

if (!is.null(sim_res$kappa_fc_mat)){
  kmat_fc <- sim_res$kappa_fc_mat
  colnames(kmat_fc) <- varnames
}

varmat_pltfcn(
  sim_res$alpha_mat,
  y_name = "alpha",
  burn = 0,
  show_vars = showvars
)$all_vars_plt

varmat_pltfcn(
  kmat_gl,
  y_name = "GLOBAL kappa",
  burn = 0,
  show_vars = showvars
)$all_vars_plt

varmat_pltfcn(
  kmat_lo,
  y_name = "LOCAL kappa",
  burn = 0,
  show_vars = showvars
)$all_vars_plt

varmat_pltfcn(
  kmat_tc,
  y_name = "tau-corrected kappas",
  burn = 0,
  show_vars = showvars
)$all_vars_plt

if (!is.null(sim_res$kappa_fc_mat)){
  varmat_pltfcn(
    kmat_fc,
    y_name = "frob-corrected kappas",
    burn = 0,
    show_vars = showvars
  )$all_vars_plt
}


err_by_max_bfdr(
  kmat_lo[nrow(kmat_lo), ],
  true_vec = true_vec
)$plt_fdrs + 
  labs(
    subtitle = "using local kappas as dropout probabilities"
  )

err_by_max_bfdr(
  kmat_gl[nrow(kmat_gl), ],
  true_vec = true_vec
)$plt_fdrs + 
  labs(
    subtitle = "using global kappas as dropout probabilities"
  )

err_by_max_bfdr(
  kmat_tc[nrow(kmat_tc),],
  true_vec = true_vec
)$plt_fdrs + 
  labs(
    subtitle = "tau-corrected kappas as dropout probabilities"
  )

if (!is.null(sim_res$kappa_fc_mat)){
  err_by_max_bfdr(
    kmat_fc[nrow(kmat_fc),],
    true_vec = true_vec
  )$plt_fdrs + 
    labs(
      subtitle = "frob-corrected kappas as dropout probabilities"
    )
}

```

#### sim 2

```{r}
load(resfile_vanilla[2])
nn_mod <- torch_load(modfile_vanilla[2])
<<VIS_CHUNK>>
```

### comments

- alphas capturing everything but z3

- local kappas getting all but z3 and (somewhat) x2

- BFDR not bad, but noise = 0 here for testing.


# VC mod testing

Explicitly modeling the VC structure:

- input $X, Z$ vars separately.  First $L-1$ layers take only $Z$ variables as input.

- First $L-1$ layers (all but last) used to estimate $\beta_j(Z)$'s and perform variable selection on the $Z$ variables;

- layer $L$ (output layer) does not have a weight matrix; only exists to estimate final scale parameters for the $\beta_j$'s / provide variable selection on the $X$ variables:

  - layer $L$ computes $\hat{y_i} = \beta_0(Z_i) \times \lambda_0 \tau_L + \sum_{j=1}^p \beta_j(Z_i) \times \lambda_j \tau_L \times x_{i,j}$
  



## 3L 8-16 VC, n=10k, sig=1


```{r VC_FNAMES_SETUP, echo = FALSE}
stem_vc0 <- "VCmod_p3_n10k_"
seeds_vc0 <- c(525655, 846743)

resfile_vc0 <- here::here(
  "sims", "results", 
  paste0(stem_vc0, seeds_vc0, ".RData")
)
modfile_vc0 <- here::here(
  "sims", "results", 
  paste0(stem_vc0, seeds_vc0, ".pt")
)
load(resfile_vc0[1])
nn_mod <- torch_load(modfile_vc0[1])
```

- data: R = 20, p = 3, n = 10k, noise = 1

- model: 3 regular hshoe layers + vc layer

- prior tau_R (used in first layer): `r `sim_res$sim_params$prior_tau_R`

- prior tau_p (used in last layer): `r `sim_res$sim_params$prior_tau_p`

- agnostic tau otherwise

- 2 hidden layers, 8 and 16 units;

- $\tau_0$ agnostic for all.

```{r}
data_desc(sim_res)
dim_list <- sim_res$sim_params[grepl("d_", names(sim_res$sim_params))]
dim_vec <- do.call(c, dim_list)
print(dim_vec)
# param_counts_from_dims is slight overcount (written for regular hshoe layers)
# subtract (d_in*d_out + 1)*2 from param counts b/c vc layer has no weights/bias
param_counts_from_dims(dim_vec) 
nn_mod$children
```



```{r VC0_PLOTTING_SETUP}
varnames <- c(
  paste0("z", 1:sim_res$sim_params$R),
  "b_int",
  paste0("b", 1:sim_res$sim_params$p)
)
showvars <- c(
  paste0("z", 1:5),
  "b_int",
  paste0("b", 1:sim_res$sim_params$p)
)
true_vec <- varnames %in% showvars
```


### results {.panelset}


```{r}
load(resfile_vc0[1])
nn_mod <- torch_load(modfile_vc0[1])
```


```{r, echo = FALSE}
sim_ind = 1
```


#### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_vc0[sim_ind])
nn_mod <- torch_load(modfile_vc0[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```


#### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_vc0[sim_ind])
nn_mod <- torch_load(modfile_vc0[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```


### comments

MSE/loss plots indicate that the models have not really converged. Actually kind of heartening that maybe it can do better, but how long will we need to train?

- weirdly both sims' plots follow roughly same trajectories

- alphas capture everything except z3

- local kappas capture  most (at very end) except z3, b2/x2

- BFDR plots not good




## 3L 8-16 VC, n = 1k, sig=1

```{r vc3l_FNAMES, echo = FALSE}
stem_vc3l <- "VCmod_3L_t1_p3_n1k_"
seeds_vc3l <- c(846743)

resfile_vc3l <- here::here(
  "sims", "results", 
  paste0(stem_vc3l, seeds_vc3l, ".RData")
)
modfile_vc3l <- here::here(
  "sims", "results", 
  paste0(stem_vc3l, seeds_vc3l, ".pt")
)

load(resfile_vc3l[1])
nn_mod <- torch_load(modfile_vc3l[1])

data_desc(sim_res)

```

- data: R = 20, p = 3, n = 10k, noise = 1

- model: 3 regular hshoe layers + vc layer

- (agnostic) prior tau_R (used in first layer): `sim_res$sim_params$prior_tau_R`

- (agnostic) prior tau_p (used in last layer): `sim_res$sim_params$prior_tau_p`

- 2 hidden layers, 8 and 16 units;

- $\tau_0$ agnostic for all.

```{r}
nn_mod$children
```


### results {.panelset}


```{r}
load(resfile_vc3l[1])
nn_mod <- torch_load(modfile_vc3l[1])
```


```{r, echo = FALSE}
sim_ind = 1
```


#### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_vc3l[sim_ind])
nn_mod <- torch_load(modfile_vc3l[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```



### comments

WEIRD.  First layer (look at $Z$-related $\kappa$'s) doesn't seem to really be learning.  Something seems wrong in BFDR plots (why is fdr non-monotonic)




## 5-L 8-16-16-16 VC, n=10k, sig=1

```{r vc5l_FNAMES, echo = FALSE}
stem_vc5l <- "VCmod_5L_t1_p3_n10k_"
seeds_vc5l <- c(846743)

resfile_vc5l <- here::here(
  "sims", "results", 
  paste0(stem_vc5l, seeds_vc5l, ".RData")
)
modfile_vc5l <- here::here(
  "sims", "results", 
  paste0(stem_vc5l, seeds_vc5l, ".pt")
)

load(resfile_vc5l[1])
nn_mod <- torch_load(modfile_vc5l[1])
```


- data: R = 20, p = 3, n = 10k, noise = 1

- model: 5 regular hshoe layers + vc layer

- (agnostic) prior tau_R (used in first layer): `sim_res$sim_params$prior_tau_R`

- (agnostic) prior tau_p (used in last layer): `sim_res$sim_params$prior_tau_p`

- 4 hidden layers, 8 and 16 units;

- $\tau_0$ agnostic for all.

```{r}
nn_mod$children
data_desc(sim_res)
```


### results {.panelset}


```{r}
load(resfile_vc5l[1])
nn_mod <- torch_load(modfile_vc5l[1])
```


```{r, echo = FALSE}
sim_ind = 1
```


#### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_vc5l[sim_ind])
nn_mod <- torch_load(modfile_vc5l[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```


### comments

- interestingly, train mse consistently higher than test mse

- not sure if converged

- alphas only get beta2, beta3, and somewhat beta1

- same with local and tau-corrected kappas


# VC $\beta$ only

- uses NN to model betas, no selection on X vars

## $\beta$s: 3L 8-16, n=1k, sig=0

```{r, echo = FALSE}
stem_vcb816 <- "VCbetas_816_sig0_p3_n1k_"
seeds_vcb816 <- c(525655, 846743)

resfile_vcb816 <- here::here(
  "sims", "results", 
  paste0(stem_vcb816, seeds_vcb816, ".RData")
)
modfile_vcb816 <- here::here(
  "sims", "results", 
  paste0(stem_vcb816, seeds_vcb816, ".pt")
)

sim_ind = 1
load(resfile_vcb816[sim_ind])
nn_mod <- torch_load(modfile_vcb816[sim_ind])

data_desc(sim_res)
```


```{r}
varnames <- paste0("z", 1:sim_res$sim_params$R)
showvars <- paste0("z", 1:5)
true_vec <- varnames %in% showvars
```


### results {.panelset}

#### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_vcb816[sim_ind])
nn_mod <- torch_load(modfile_vcb816[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```



#### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_vcb816[sim_ind])
nn_mod <- torch_load(modfile_vcb816[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```



### comments

- obvious problems --- doesn't appear to be learning at all.  Possibly gradient lost from computing $\sum_j \beta_j (Z) X_j$ outside of NN?


## retry: 3L 8-16, n=1k, sig=0

- computing summation within network

```{r, echo = FALSE}
stem_vcb816 <- "VCbetas2_816_sig0_p3_n1k_"
seeds_vcb816 <- c(525655, 846743)

resfile_vcb816 <- here::here(
  "sims", "results", 
  paste0(stem_vcb816, seeds_vcb816, ".RData")
)
modfile_vcb816 <- here::here(
  "sims", "results", 
  paste0(stem_vcb816, seeds_vcb816, ".pt")
)

sim_ind = 1
load(resfile_vcb816[sim_ind])
nn_mod <- torch_load(modfile_vcb816[sim_ind])
data_desc(sim_res)
```


### results {.panelset}

#### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_vcb816[sim_ind])
nn_mod <- torch_load(modfile_vcb816[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```



#### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_vcb816[sim_ind])
nn_mod <- torch_load(modfile_vcb816[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```



### comments

issue persists....




## $\beta$'s: 3L 32-16, n=1k, sig=0


```{r, echo = FALSE}
stem_vcb3216 <- "VCbetas2_3216_sig0_p3_n1k_"
seeds_vcb3216 <- c(86961, 963471)

resfile_vcb3216 <- here::here(
  "sims", "results", 
  paste0(stem_vcb3216, seeds_vcb3216, ".RData")
)
modfile_vcb3216 <- here::here(
  "sims", "results", 
  paste0(stem_vcb3216, seeds_vcb3216, ".pt")
)



sim_ind = 1
load(resfile_vcb3216[sim_ind])
nn_mod <- torch_load(modfile_vcb3216[sim_ind])
data_desc(sim_res)

```


### results {.panelset}

#### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_vcb3216[sim_ind])
nn_mod <- torch_load(modfile_vcb3216[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```



#### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_vcb3216[sim_ind])
nn_mod <- torch_load(modfile_vcb3216[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```



### comments:

tried fiddling with learning rate, still nothing.  Must be a calculation error somewhere which will take more work to find.






# 2nd sims set: Vanilla

```{r, echo = FALSE}
varnames <- c(
  paste0("z", 1:sim_res$sim_params$R),
  paste0("x", 1:sim_res$sim_params$p)
)
showvars <- c(
  paste0("z", 1:5),
  paste0("x", 1:3)
)
true_vec <- varnames %in% showvars
```


## sig0, n10k, 16-32

```{r, echo = FALSE}
stem_vanilla1632_10k <- "VC_vanilla1632_agnostic_test0sig_p3_n10k_"
seeds_vanilla1632_10k <- c(69530, 846514)

resfile_vanilla1632_10k <- here::here(
  "sims", "results", 
  paste0(stem_vanilla1632_10k, seeds_vanilla1632_10k, ".RData")
)
modfile_vanilla1632_10k <- here::here(
  "sims", "results", 
  paste0(stem_vanilla1632_10k, seeds_vanilla1632_10k, ".pt")
)

sim_ind = 1
load(resfile_vanilla1632_10k[sim_ind])
nn_mod <- torch_load(modfile_vanilla1632_10k[sim_ind])
data_desc(sim_res)

```


### results {.panelset}

#### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_vanilla1632_10k[sim_ind])
nn_mod <- torch_load(modfile_vanilla1632_10k[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```



#### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_vanilla1632_10k[sim_ind])
nn_mod <- torch_load(modfile_vanilla1632_10k[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```



### comments:

- alphas, local kappas: pick up on most except z3, x1

- tau-corr kappas: don't get z3, x1, x2

- BFDR's: not terrible, but requires high BFDR to get most True Pos's

- may have benefitted from further training



## sig0, n10k, 128-64

```{r, echo = FALSE}
stem_vanilla12864_10k <- "VC_vanilla12864_agnostic_test0sig_p3_n10k_"
seeds_vanilla12864_10k <- c(513339, 999784)

resfile_vanilla12864_10k <- here::here(
  "sims", "results", 
  paste0(stem_vanilla12864_10k, seeds_vanilla12864_10k, ".RData")
)
modfile_vanilla12864_10k <- here::here(
  "sims", "results", 
  paste0(stem_vanilla12864_10k, seeds_vanilla12864_10k, ".pt")
)

sim_ind = 1
load(resfile_vanilla12864_10k[sim_ind])
nn_mod <- torch_load(modfile_vanilla12864_10k[sim_ind])
data_desc(sim_res)

```


### results {.panelset}

#### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_vanilla12864_10k[sim_ind])
nn_mod <- torch_load(modfile_vanilla12864_10k[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```



#### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_vanilla12864_10k[sim_ind])
nn_mod <- torch_load(modfile_vanilla12864_10k[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```



### comments:

- may have benefitted from further training

- alphas get everything but z3

- tau-kappas not picking up z3, x1, x2 well

- BFDR is OK






# 2nd sims set: VCMod

## sig 0, n 10k, 8-16

```{r, echo = FALSE}
stem_vcmod816_sig0 <- "VCmod_3L_test0sig_p3_n10k_"
seeds_vcmod816_sig0 <- c(525655, 846743)

resfile_vcmod816_sig0 <- here::here(
  "sims", "results", 
  paste0(stem_vcmod816_sig0, seeds_vcmod816_sig0, ".RData")
)
modfile_vcmod816_sig0 <- here::here(
  "sims", "results", 
  paste0(stem_vcmod816_sig0, seeds_vcmod816_sig0, ".pt")
)

sim_ind = 1
load(resfile_vcmod816_sig0[sim_ind])
nn_mod <- torch_load(modfile_vcmod816_sig0[sim_ind])
data_desc(sim_res)
sim_res$alpha_mat
sim_res$kappa_mat
```



```{r, echo = FALSE}
varnames <- c(
  paste0("z", 1:sim_res$sim_params$R),
  "b_int",
  paste0("b", 1:sim_res$sim_params$p)
)
showvars <- c(
  paste0("z", 1:5),
  "b_int",
  paste0("b", 1:3)
)
true_vec <- varnames %in% showvars
```



### results {.panelset}

#### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_vcmod816_sig0[sim_ind])
nn_mod <- torch_load(modfile_vcmod816_sig0[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```



#### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_vcmod816_sig0[sim_ind])
nn_mod <- torch_load(modfile_vcmod816_sig0[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```



### comments:

- maybe converged?

- alphas get everything except z3

- tau-kappas not great; don't get b0, b1, b2, z3

- puzzling why alphas are so different than the kappas





## sig 0, n 10k, 128-64

```{r, echo = FALSE}
stem_vcmod12864_sig0 <- "VCmod_3L_12864_test0sig_p3_n10k_"
seeds_vcmod12864_sig0 <- c(222169, 95549)

resfile_vcmod12864_sig0 <- here::here(
  "sims", "results", 
  paste0(stem_vcmod12864_sig0, seeds_vcmod12864_sig0, ".RData")
)
modfile_vcmod12864_sig0 <- here::here(
  "sims", "results", 
  paste0(stem_vcmod12864_sig0, seeds_vcmod12864_sig0, ".pt")
)

sim_ind = 1
load(resfile_vcmod12864_sig0[sim_ind])
nn_mod <- torch_load(modfile_vcmod12864_sig0[sim_ind])
data_desc(sim_res)

```



```{r, echo = FALSE}
varnames <- c(
  paste0("z", 1:sim_res$sim_params$R),
  "b_int",
  paste0("b", 1:sim_res$sim_params$p)
)
showvars <- c(
  paste0("z", 1:5),
  "b_int",
  paste0("b", 1:3)
)
true_vec <- varnames %in% showvars
```



### results {.panelset}

#### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_vcmod12864_sig0[sim_ind])
nn_mod <- torch_load(modfile_vcmod12864_sig0[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```



#### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_vcmod12864_sig0[sim_ind])
nn_mod <- torch_load(modfile_vcmod12864_sig0[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```



### comments:

- interestingly train_mse > test_mse again (similar to 5-layer model, VCBetas models)

- alphas get all but z3

- local kappas: don't get z3, b1; b_int hovers around 0.5

- tau-kappas: don't get z3, any of the betas


# 2nd sims EXP 2: vanilla, p=50


## sig0, n10k, 128-64

```{r, echo = FALSE}
stem_vanilla12864_10k_e2 <- "VC_vanilla12864_agnostic_test0sigexp2_p50_n10k_"
seeds_vanilla12864_10k_e2 <- c(513339, 999784)

resfile_vanilla12864_10k_e2 <- here::here(
  "sims", "results", 
  paste0(stem_vanilla12864_10k_e2, seeds_vanilla12864_10k_e2, ".RData")
)
modfile_vanilla12864_10k_e2 <- here::here(
  "sims", "results", 
  paste0(stem_vanilla12864_10k_e2, seeds_vanilla12864_10k_e2, ".pt")
)

sim_ind = 1
load(resfile_vanilla12864_10k_e2[sim_ind])
nn_mod <- torch_load(modfile_vanilla12864_10k_e2[sim_ind])

varnames <- c(
  paste0("z", 1:sim_res$sim_params$R),
  paste0("x", 1:sim_res$sim_params$p)
)
showvars <- c(
  paste0("z", 1:5),
  paste0("x", 1:3)
)
true_vec <- varnames %in% showvars

data_desc(sim_res)

```


### results {.panelset}

#### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_vanilla12864_10k_e2[sim_ind])
nn_mod <- torch_load(modfile_vanilla12864_10k_e2[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```



#### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_vanilla12864_10k_e2[sim_ind])
nn_mod <- torch_load(modfile_vanilla12864_10k_e2[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```



### comments:

- could probably benefit from further training?

- alphas & local kappas don't get z3, x1 on wrong trajectory

- BFDR isn't terrible



## REAL: sig = 1, n = 1k, 3232

```{r, echo = FALSE}
stem_vanilla3232_e2 <- "VC_vanilla3232_agnostic_exp2_p50_n1k_"
seeds_vanilla3232_e2 <- c(416363, 506288)

resfile_vanilla3232_e2 <- here::here(
  "sims", "results", 
  paste0(stem_vanilla3232_e2, seeds_vanilla3232_e2, ".RData")
)
modfile_vanilla3232_e2 <- here::here(
  "sims", "results", 
  paste0(stem_vanilla3232_e2, seeds_vanilla3232_e2, ".pt")
)

sim_ind = 1
load(resfile_vanilla3232_e2[sim_ind])
nn_mod <- torch_load(modfile_vanilla3232_e2[sim_ind])
data_desc(sim_res)

```


### results {.panelset}

#### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_vanilla3232_e2[sim_ind])
nn_mod <- torch_load(modfile_vanilla3232_e2[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```



#### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_vanilla3232_e2[sim_ind])
nn_mod <- torch_load(modfile_vanilla3232_e2[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```



### comments:

- could have used further training

- alphas & local: worst so far: doesn't get x1, x2, z3, z5

- tau-kappas have clearer separation but same mistakes as alphas, local

- BFDR is ok-ish, but needs high BFDR to get TPs






# 2nd sims EXP 2: VCMod

## sig 0, n 10k, 128-64, p=50

```{r, echo = FALSE}
stem_vcmod12864_sig0_e2 <- "VCmod_3L_12864_test0sig_exp2_p50_n10k_"
seeds_vcmod12864_sig0_e2 <- c(222169, 95549)

resfile_vcmod12864_sig0_e2 <- here::here(
  "sims", "results", 
  paste0(stem_vcmod12864_sig0_e2, seeds_vcmod12864_sig0_e2, ".RData")
)
modfile_vcmod12864_sig0_e2 <- here::here(
  "sims", "results", 
  paste0(stem_vcmod12864_sig0_e2, seeds_vcmod12864_sig0_e2, ".pt")
)

sim_ind = 1
load(resfile_vcmod12864_sig0_e2[sim_ind])
nn_mod <- torch_load(modfile_vcmod12864_sig0_e2[sim_ind])
data_desc(sim_res)

```



```{r, echo = FALSE}
varnames <- c(
  paste0("z", 1:sim_res$sim_params$R),
  "b_int",
  paste0("b", 1:sim_res$sim_params$p)
)
showvars <- c(
  paste0("z", 1:5),
  "b_int",
  paste0("b", 1:3)
)
true_vec <- varnames %in% showvars
```



### results {.panelset}

#### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_vcmod12864_sig0_e2[sim_ind])
nn_mod <- torch_load(modfile_vcmod12864_sig0_e2[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```



#### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_vcmod12864_sig0_e2[sim_ind])
nn_mod <- torch_load(modfile_vcmod12864_sig0_e2[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```



### comments:

- MSE a bit higher than usual (actual sig = 0)

- alphas pick up b1, b2, b3 but nothing else

- same with local kappas

- tau-corrected kappas all travel together, basically the reverse of the local kappas which is WEIRD

- lots of weirdness in BFDR plots... ???




## REAL: sig 1, n 10k, 32-32, p=50

```{r, echo = FALSE}
stem_vcmod3232_e2 <- "VCmod_3L_3232_exp2_p50_n10k_"
seeds_vcmod3232_e2 <- c(222169, 95549)

resfile_vcmod3232_e2 <- here::here(
  "sims", "results", 
  paste0(stem_vcmod3232_e2, seeds_vcmod3232_e2, ".RData")
)
modfile_vcmod3232_e2 <- here::here(
  "sims", "results", 
  paste0(stem_vcmod3232_e2, seeds_vcmod3232_e2, ".pt")
)

sim_ind = 1
load(resfile_vcmod3232_e2[sim_ind])
nn_mod <- torch_load(modfile_vcmod3232_e2[sim_ind])
data_desc(sim_res)

```



```{r, echo = FALSE}
varnames <- c(
  paste0("z", 1:sim_res$sim_params$R),
  "b_int",
  paste0("b", 1:sim_res$sim_params$p)
)
showvars <- c(
  paste0("z", 1:5),
  "b_int",
  paste0("b", 1:3)
)
true_vec <- varnames %in% showvars
```



### results {.panelset}

#### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_vcmod3232_e2[sim_ind])
nn_mod <- torch_load(modfile_vcmod3232_e2[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```



#### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_vcmod3232_e2[sim_ind])
nn_mod <- torch_load(modfile_vcmod3232_e2[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```



### comments:

- loss still decreasing - probably should not have stopped training

- alphas, local kappas looking excellent, except z3 (as usual)

- tau-corrected kappas weirdly very different, only getting the z-variables (except z3)

- A correction on the final-layer-estimated kappas seems motivated.  (notably, those do not actually get a tau-correction)






