---
title: "VC data, first sim results"
author: "Arnie Seong"
date: "`r format(Sys.time(), '%d %B %Y')`"
header-includes:
  - \usepackage{bm}
  - \usepackage{xcolor}
  - \usepackage{amssymb}
output: 
  html_document:
    df_print: paged
    theme: cerulean
    highlight: tango
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: true
    code_fold: show
urlcolor: blue
editor_options: 
  chunk_output_type: console
---

<style>
  .panel-tabs{
    opacity: 1;
    background-color: #2fa4e7;
      color: #ffffff;
      position: sticky;
    top: 0
  }
</style>
  

```{r setup, include=FALSE, message=F, echo=F, warning=F}
# LIBRARIES----

#### plotting:
library(ggplot2)
library(gridExtra)

# #### Misc:
library(here)
library(tidyr)
library(knitr)
library(kableExtra)
library(dplyr)

# model packages
library(torch)

# DOCUMENT SETUP ----
# detect pdf/html output, set chunk options, sci.notation 
latex_out <- knitr::is_latex_output()
knitr::opts_chunk$set(
  cache = FALSE, 
  message = FALSE, 
  echo = !knitr::is_latex_output(), 
  warning = FALSE
)


if (knitr::is_latex_output()) {
  knitr::opts_chunk$set(fig.height=4, 
                        fig.width=6)
} else {
  knitr::opts_chunk$set(out.width = "100%")
}

options(scipen=10)

# PANELSET
xaringanExtra::use_panelset()
xaringanExtra::style_panelset_tabs(font_family = "inherit")



# TEXT/TABLE FORMATTING----

custom_purple <- ifelse(
  knitr::is_latex_output(),
  "purple",
  "#b51ced"
)

custom_blue <- ifelse(
  knitr::is_latex_output(),
  "blue",
  "#11579e"
)

colorize <- function(x, color=custom_purple) {
  # text color conditional on latex/html output
  # from rmarkdown cookbook
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{ %s}{ %s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color, x)
  } else x
}

cat_color <- function(txt, style = 1, color = 36){
  cat(
    paste0(
      "\033[0;",
      style, ";",
      color, "m",
      txt,
      "\033[0m","\n"
    )
  )  
}

# kable NA handling
options(knitr.kable.NA = '')

# mykable function
mykable <- function(tab, cap,
                    latex_options=c("hold_position", "scale_down", "striped"), 
                    bootstrap_options=c("striped", "hover", "condensed"), 
                    full_width=F, position="center", ...){
  # kable formatting conditional on latex or html output
  if (is.null(getOption("knitr.in.progress"))){
    print(tab)
  } else if (knitr::is_latex_output()){
    kable(x=tab, caption=cap, ...) %>%
      kableExtra::kable_styling(latex_options = latex_options)
  } else if (knitr::is_html_output()){
    kable(x=tab, caption=cap, ...) %>%
      kableExtra::kable_styling(bootstrap_options = bootstrap_options, full_width=full_width, position=position)
  }
}

# notin
`%notin%` <- Negate(`%in%`)

library(torch)
source(here("Rcode", "torch_horseshoe_klcorrected.R"))
source(here("Rcode", "sim_functions.R"))
source(here("Rcode", "analysis_fcns.R"))
source(here("Rcode", "sparseVCBART_fcns.R"))
source(here("Rcode", "torch_VC_outputlayer.R"))
```





# testing the VC waters

- $Z$ dimension $R$ = 20, results only depend on first 5 $Z$ variables,

- $X$ dimension $p$ = 3,

Just to see if we can adequately capture the data generating functions, tested with $n = 10k$, noise variance $\sigma^2_\epsilon = 0$

## vanilla model

Just proceeding as usual without explicitly modeling the VC structure:


```{r FNAMES_SETUP, echo = FALSE}
stem_vanilla <- "VC_vanilla816_agnostic_test0sig_p3_n10k_"
seeds_vanilla <- c(525655, 846743)
resfile_vanilla <- here::here(
  "sims", "results", 
  paste0(stem_vanilla, seeds_vanilla, ".RData")
)
modfile_vanilla <- here::here(
  "sims", "results", 
  paste0(stem_vanilla, seeds_vanilla, ".pt")
)
# VCmod_p3_n10k_846743 and _525655

```


- 2 hidden layers, 8 and 16 units;

- $\tau_0$ agnostic for all.

```{r}
load(resfile_vanilla[1])
nn_mod <- torch_load(modfile_vanilla[1])
plot_b0_true()
plot_b1_true()

sim_res$sim_params$p_0
dim_vec <- c(
  sim_res$sim_params$d_0,
  sim_res$sim_params$d_1,
  sim_res$sim_params$d_2,
  sim_res$sim_params$d_L
)
param_counts_from_dims(dim_vec)
```



```{r PLOTTING_SETUP}
varnames <- c(
  paste0("z", 1:sim_res$sim_params$R),
  paste0("x", 1:sim_res$sim_params$p)
)
showvars <- c(
  paste0("z", 1:5),
  paste0("x", 1:sim_res$sim_params$p)
)
true_vec <- varnames %in% showvars
```


### results {.panelset}

  
  
#### sim 1
  
```{r VIS_CHUNK}
loss_pltfcn(sim_res, burn = 5e4)$mse_plt
loss_pltfcn(sim_res, burn = 5e4)$kl_plt

kmat_tc <- sim_res$kappa_tc_mat
kmat_gl <- sim_res$kappa_mat
kmat_lo <- sim_res$kappa_local_mat
kmat_fc <- sim_res$kappa_fc_mat

colnames(sim_res$alpha_mat)  <- 
  colnames(kmat_tc) <- 
  colnames(kmat_gl) <-
  colnames(kmat_lo) <- varnames

if (!is.null(sim_res$kappa_fc_mat)){
  kmat_fc <- sim_res$kappa_fc_mat
  colnames(kmat_fc) <- varnames
}

varmat_pltfcn(
  sim_res$alpha_mat,
  y_name = "alpha",
  burn = 0,
  show_vars = showvars
)$all_vars_plt

varmat_pltfcn(
  kmat_gl,
  y_name = "GLOBAL kappa",
  burn = 0,
  show_vars = showvars
)$all_vars_plt

varmat_pltfcn(
  kmat_lo,
  y_name = "LOCAL kappa",
  burn = 0,
  show_vars = showvars
)$all_vars_plt

varmat_pltfcn(
  kmat_tc,
  y_name = "tau-corrected kappas",
  burn = 0,
  show_vars = showvars
)$all_vars_plt

if (!is.null(sim_res$kappa_fc_mat)){
  varmat_pltfcn(
    kmat_fc,
    y_name = "frob-corrected kappas",
    burn = 0,
    show_vars = showvars
  )$all_vars_plt
}


err_by_max_bfdr(
  kmat_lo[nrow(kmat_lo), ],
  true_vec = true_vec
)$plt_fdrs + 
  labs(
    subtitle = "using local kappas as dropout probabilities"
  )

err_by_max_bfdr(
  kmat_gl[nrow(kmat_gl), ],
  true_vec = true_vec
)$plt_fdrs + 
  labs(
    subtitle = "using global kappas as dropout probabilities"
  )

err_by_max_bfdr(
  kmat_tc[nrow(kmat_tc),],
  true_vec = true_vec
)$plt_fdrs + 
  labs(
    subtitle = "tau-corrected kappas as dropout probabilities"
  )

if (!is.null(sim_res$kappa_fc_mat)){
  err_by_max_bfdr(
    kmat_fc[nrow(kmat_fc),],
    true_vec = true_vec
  )$plt_fdrs + 
    labs(
      subtitle = "frob-corrected kappas as dropout probabilities"
    )
}

```

#### sim 2

```{r}
load(resfile_vanilla[2])
nn_mod <- torch_load(modfile_vanilla[2])
<<VIS_CHUNK>>
```



# VC mod testing

Explicitly modeling the VC structure:

- input $X, Z$ vars separately.  First $L-1$ layers take only $Z$ variables as input.

- First $L-1$ layers (all but last) used to estimate $\beta_j(Z)$'s and perform variable selection on the $Z$ variables;

- layer $L$ (output layer) does not have a weight matrix; only exists to estimate final scale parameters for the $\beta_j$'s / provide variable selection on the $X$ variables:

  - layer $L$ computes $\hat{y_i} = \beta_0(Z_i) \times \lambda_0 \tau_L + \sum_{j=1}^p \beta_j(Z_i) \times \lambda_j \tau_L \times x_{i,j}$
  



## first VC sim


```{r VC_FNAMES_SETUP, echo = FALSE}
stem_vc0 <- "VCmod_p3_n10k_"
seeds_vc0 <- c(525655, 846743)

resfile_vc0 <- here::here(
  "sims", "results", 
  paste0(stem_vc0, seeds_vc0, ".RData")
)
modfile_vc0 <- here::here(
  "sims", "results", 
  paste0(stem_vc0, seeds_vc0, ".pt")
)
load(resfile_vc0[1])
nn_mod <- torch_load(modfile_vc0[1])
```

- data: R = 20, p = 3, n = 10k, noise = 0

- model: 3 regular hshoe layers + vc layer

- prior tau_R (used in first layer): `sim_res$sim_params$prior_tau_R`

- prior tau_p (used in last layer): `sim_res$sim_params$prior_tau_p`

- agnostic tau otherwise

- 2 hidden layers, 8 and 16 units;

- $\tau_0$ agnostic for all.

```{r}
sim_res$sim_params
dim_list <- sim_res$sim_params[grepl("d_", names(sim_res$sim_params))]
dim_vec <- do.call(c, dim_list)
print(dim_vec)
# param_counts_from_dims is slight overcount (written for regular hshoe layers)
# subtract (d_in*d_out + 1)*2 from param counts b/c vc layer has no weights/bias
param_counts_from_dims(dim_vec) 
nn_mod$children
```



```{r VC0_PLOTTING_SETUP}
varnames <- c(
  paste0("z", 1:sim_res$sim_params$R),
  "b_int",
  paste0("b", 1:sim_res$sim_params$p)
)
showvars <- c(
  paste0("z", 1:5),
  "b_int",
  paste0("b", 1:sim_res$sim_params$p)
)
true_vec <- varnames %in% showvars
```


### results {.panelset}


```{r}
load(resfile_vc0[1])
nn_mod <- torch_load(modfile_vc0[1])
```


```{r, echo = FALSE}
sim_ind = 1
```


#### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_vc0[sim_ind])
nn_mod <- torch_load(modfile_vc0[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```


#### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_vc0[sim_ind])
nn_mod <- torch_load(modfile_vc0[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```


### comments

MSE/loss plots look __nowhere near convergence.__  Actually kind of heartening that maybe it can do better, but how long will we need to train?  Increase the learning rate a bunch.






## all agnostic 3L VC sim

```{r vc3l_FNAMES, echo = FALSE}
stem_vc3l <- "VCmod_3L_t1_p3_n1k_"
seeds_vc3l <- c(846743)

resfile_vc3l <- here::here(
  "sims", "results", 
  paste0(stem_vc3l, seeds_vc3l, ".RData")
)
modfile_vc3l <- here::here(
  "sims", "results", 
  paste0(stem_vc3l, seeds_vc3l, ".pt")
)

load(resfile_vc3l[1])
nn_mod <- torch_load(modfile_vc3l[1])
```

- data: R = 20, p = 3, n = 10k, noise = 0

- model: 3 regular hshoe layers + vc layer

- (agnostic) prior tau_R (used in first layer): `sim_res$sim_params$prior_tau_R`

- (agnostic) prior tau_p (used in last layer): `sim_res$sim_params$prior_tau_p`

- 2 hidden layers, 8 and 16 units;

- $\tau_0$ agnostic for all.

```{r}
nn_mod$children
```


### results {.panelset}


```{r}
load(resfile_vc3l[1])
nn_mod <- torch_load(modfile_vc3l[1])
```


```{r, echo = FALSE}
sim_ind = 1
```


#### sim `r sim_ind`

```{r, echo = FALSE}
load(resfile_vc3l[sim_ind])
nn_mod <- torch_load(modfile_vc3l[sim_ind])
<<VIS_CHUNK>>
sim_ind = sim_ind + 1
```



### comments

Terrible.  First layer (look at $Z$-related $\kappa$'s) doesn't seem to really be learning.



